%------------------------------------------------------------------------------

\documentclass[12pt]{article}
\renewcommand{\baselinestretch}{1.5}
\usepackage{sectsty,setspace}
% \renewcommand*{\thefootnote}{\fnsymbol{footnote}}
\usepackage{sectsty,setspace} 
\usepackage[top=1.87cm, bottom=1.87cm, left=1.87cm, right=1.87cm]{geometry} 
\usepackage{epstopdf} % for pdf creation
\usepackage{amsmath,latexsym,amssymb,wasysym} % improving structure
\usepackage{cite}
%\usepackage{citesupernumber}
%\usepackage{citecollapse}
%\usepackage{hyperref}
\usepackage{float} % for figures and tables
\usepackage[sort&compress, super, numbers]{natbib}
\floatstyle{plaintop}
\restylefloat{table}
%\usepackage[table]{xcolor} % http://ctan.org/pkg/xcolor
\usepackage{times} % setting font to times
\setstretch{1.1}
\setlength{\baselineskip}{0.167in} 
\setlength\parindent{0pt} % no indents throughout
%------------------------------------------------------------------------------
\begin{document}
\section*{Fueling Next Year's Growth of Trees with Carbon and Nitrogen}
\textbf {Context:} %emw9Nov -- move the punctuation before the superscript captions and remove white space -- see example change I made in second sentence. 
In temperate and boreal forests, temperature plays a crucial role in setting the boundaries for seasonal physiological activity. Thus, with rising temperatures from anthropogenic climate change, the climatically possible growing season has lengthened in many ecosystems worldwide by up to 11 days.\citep{korner_phenology_2010, menzel_growing_1999} Plants have tracked this through shifts in phenology—the study of recurring life history events—which are expected to continue with increasing temperatures.\citep{wolkovich_warming_2012} In particular, trees have shifted earlier in the spring and may use these extra days to fix more carbon and increase growth during the current growing season.\citep{keenan_net_2014, wang_interactive_2020} At the same time, fall events in trees (e.g., leaf senescence) have been delayed, but the impacts on their fitness are not well understood. Together earlier spring and delayed fall events are often hypothesized to affect growth in the next growth season. This is rarely tested, however, and tests to date have used adult trees where many co-varying factors make teasing out the effect of longer seasons difficult. Here, I propose an extended season experiment using saplings to mechanistically test this critical hypothesis. My proposed work will provide valuable insight into the regeneration capacity of forests under a warming climate, considering the importance of young trees on forest recruitment.\citep{zohner_how_2021} \\
\textbf {Research Question:} How do extended growing seasons affect tree growth across different species both immediately (in the same year as the extended season) and in subsequent years? \\
\textbf {Hypothesis:} I hypothesize that an extension of the growing season could modify a tree’s capacity to fill carbon and nitrogen storage pools.\citep{chapin_ecology_1990, lawrence_variable_2018} Trees that use this opportunity by fixing more carbon may experience increased growth in the subsequent growing season.\citep{landhausser_partitioning_2012, martens_first-year_2007} Thus, species capable of accumulating nutrients after growth cessation while going through leaf senescence might exhibit growth increment in the following growing season.\citep{schott_premature_2013} \\
\textbf {Objectives:} First, I aim to assess tree species' potential to prolong or stretch their activity schedule. Second, I will determine whether trees can absorb nutrients beyond their theoretical growing season. I will also examine if increased carbon pools translate into greater growth increment in the following growing season. Finally, I will investigate potential variations in these responses across deciduous and evergreen species, to test whether different patterns emerge within these distinct groups.\\ %emw9Nov -- I feel already that there is too much passive voice in this proposal. It's easy fix in the methods so please do (I conducted experiments in 2024...)
\textbf {Methodology:} To investigate the impact of manipulated spring and fall temperatures on phenological responses, I conducted experiments in 2024 across seven different tree species under controlled conditions, including species that span both fast and short-life strategies (e.g., \emph{Populus balsamifera}) and slow growth and longer lifespan species (e.g., \emph{Quercus macrocarpa}) and including both deciduous and evergreen species.\citep{jonsson_annual_2010} I used a full factorial design of spring and fall warming with two levels each (control/warmed) resulting in four treatments plus an additional two treatments to test fall nutrient effects, using 15 replicates each for a total of 630 individual trees. % emwNov5: could add here the total and that though this is high you have successfully managed it for one season already ... I would be honest about years and say you started it and will complete it in January 2026. crdNov7: changed dates and removed the sentence about nutrient enrichment %emw9Nov -- 4 treatments x 15 reps x 7 spp = 420 individual trees... what am I missing? I think you need to add mention of the nutrient treatments? Maybe:  
% I used a full factorial experiment of spring and fall warming with two levels each (control/warmed) resulting in four treatments plus an additional two treatments to test fall nutrient effects, using 15 replicates each (15 reps x 6 treatments x 7 species = 630 trees). 
Throughout the growing season of 2024, I tracked phenological events weekly from the start of the spring treatments through the end of the fall treatments. During the growing season of 2025, the same measurements will be performed. In fall 2025, after the trees have grown in ambient temperatures for the season, I will assess growth on the individual (total biomass) and the cellular level (number of cells and their characteristics), using dendrochronological methods.\\
\textbf{Research outreach:} Given the widespread impacts of climate change on ecosystems, understanding how forest communities respond to prolonged growing seasons is crucial. Observing the reactions of deciduous and conifer species to extended seasons may reveal potential benefits for some species and harm for others. These shifts are likely to influence forest stand dynamics across North America.

% References
\bibliographystyle{amnat.bst} % set citation style 
\bibliography{2024-CGSM.bib}


\end{document}
