`\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{June 3, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Started the day by answering many emails. I answered the git issue on nutrient depletion which took my quite some time. I also finished installing the dendrometer. I did this just so I can check if they are all working.
Met with Mao at 3:30pm to discuss worklearn. We updated the offer and will send to Lizzie to confirm the info with her. 
I checked in with Dan regarding mildew on the Acne. They don't look great right now. He told me it can take up to a week before we see any improvement. Also, I thought we had the same problem with Prvi, but its just residu of the fongicide on their leaves. 

\def\day{\textit{June 4, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Everyone from the lab}
Reifel Bird Sanctuary retreat. When we arrived, it was raining a bit, but it slowed down after 15 minutes. It was very quiet. Justin will do a slideshow of the pictures that were taken. I started working for real at 3pm. I added 2 notes to my slipbox! It was on the paper Fredi shared in git issue 14 about how to define stress in plants. I still need to cross-reference those. After this, I replied to a couple of emails that Lizzie and Christine sent me about my expense report. It took me about an hour to get this done. 

\def\day{\textit{June 5, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I went to get the Subaru serviced. I also filled up the gas tank. While I was waiting, I finished what Christine told me to do to get my expense report done. I also registered to my classes in the fall. I talked to Deirdre on my way back to talk about my talk with Christine which was very difficult. We had an idea of getting a list of things over the course of the summer of things that Deirdre should teach us.
TO DO TODAY
\begin{itemize}
    \item Scan the receipts from yesterday (dominos and rbs) -- done 
    \item Scan the receipts from today (Chevron and Kon auto) -- done
    \item Go back downstairs to grab the ziplock in the Xterra with the maintenance. Add maintenance to Git? -- done 
    \item Start a list of things Deirdre should pass on to us. -- done 
\end{itemize}

\def\day{\textit{June 6, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Lizzie and I met over Zoom in the morning to discuss many things. Details are in my notes. Main conclusion is that we will drop using the dendrometers in the fall and I should reach out to the people at OpensLab to see if they can help me troubleshoot the dendrometers. We also talked about which classes I should and shouldn't take in the fall. We talked about the nutrients and I told her that I was concerned trees were showing nutrient stress symptoms. So she gave me green light to give them liquid nutrients. I searched lots of papers to figure out what would be a good nutrient concentration to add to the trees because we want to mimic natural conditions. I asked Dan's opinion and he brought fertilizer from the greenhouse. In his opinion, this will work perfectly and will provide fast release nutrients to the plants. 
Mao and I met at 3pm, so I can show her how to take the shoot elongation measurements and finish the pheno monitoring. We had to leave before we finished because we had a lab meeting. We presented the trips we had been doing in the following weeks. I came back to Totem after to finish phenomonitoring and take the measurements on the paper rulers. 

\def\day{\textit{June 7, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Started at 10am. I kept on looking at how much fertilizer I should add to the trees. It's very ambigous, so I decided to add very small amounts at first and readjust later on. For now, I diluted the solution Dan gave me by half with tap water. I added ~125mL of liquid fertilizer to all plants today. In the afternoon, I downloaded all the data from the hobo loggers that were already in the greenhouse. Then, I added 22 temp/light hobo sensors all over the greenhouse, because I strongly suspect that we will have a big light effect because of the forest behind the greenhouse. The plants at the front of the greenhouse most likely receive much more light than the ones at the back of the greenhouse. I also took some time to move my bird feeders because I caught a squirrel eating in them. 
\begin{itemize}
	\item Figure out fertilization and do it -- done
	\item Reserve camping
	\item deliver Mao's package -- done
	\item
\end{itemize}

\def\day{\textit{June 7, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at noon, mainly to take care of the plants at Totem. I finished setting up the light meters. I decided to remove logging in the temperature data,  because anyway it's extremely biased because the sun directly hits them and make them really hot. I need to finish the greenhouse design with them in. 

\def\day{\textit{June 10, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
\begin{itemize}
	\item check new hobo sensors -- done
	\item update the greenhouse arrangement with all the new loggers
	\item make sure irrigation is back on -- done
	\item start writing up the methodology on hobo loggers and fertilizer -- done
	\item shoot elongation protocole -- done
	\item DEFENETILY do the apical shoot death monitoring -- done
	\item Write to Mao to tell her what she will need to do -- done
	\item phenomonitoring -- done
	\item load shoot elongation measurements in excel file -- done
	\item write to Lizzie and colleagues to tell them that I won't be checking my email -- done
	\item Move Alru back to the soil pit -- done
	\item Weed all the plans -- done
	\item update the pheno monitoring and shoot elongation of all the segi that I removed from the experiment. 
	\item Email Lizzie about her class-- done
	\item return book to Amazon
	\item Add notes to the labgit on chambers
	\item email Melina regarding the greenhouse -- done
	\item Inventory of trees outside at Totem -- done
	\item Clean up the mess at Totem -- done
	\item Answer Lizzie's email on Google Drive issue. -- done
	\item start loggers at the top of Greenhouse -- done
	\item add csv file description for aserdiversity -- done
	\item text dan to spray again -- done
\end{itemize}
I worked a lot on the methodology today. I wrote up on the hobo loggers, fertilization, shoot elongation monitoring. I also added a file of apical shoot monitoring because many trees have a dead apical shoot. Therefore, I don't think we will be able to estimate their inital biomass. 
\par I followed up on the git issue regarding fertilization
\par Asevdiversity: reuploaded the methodology text and added column description to the .tex file as requested by Lizzie. 
\par Big day! I did pretty much all the things I listed today! I finished with weeding all the plants in and out the greenhouse. I replied to Lizzie and Mao to finish. Break is tomorrow!

\def\day{\textit{June 11, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 12, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 13, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 14, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 17, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 18, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Vacation
\def\day{\textit{June 19, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Hectic mess with the UBC residences. They kicked me out of my place on my last day of vacation and I needed to fix this issue in the morning. Therefore I arrived at the office around 11. 
\par Read all the emails I received during my holidays and. Following is the to do list I need to do today:
\begin {itemize}
	\item Start git issue on the tree inventory
	\item update the greenhouse arrangement with all the new loggers -- done
	\item update the pheno monitoring and shoot elongation of all the segi that I removed from the experiment -- done
	\item Add notes to the labgit on chambers
	\item elongation monitoring -- done
	\item check hobo loggers with the lights --done 
	\item check hobo temperature loggers and replace the one that isn't working -- done 
	\item contact opens lab to trouble shoot the dendrometers

I noticed Mao didn't do phenomonitoring last Thursday (doy165). It's not a big deal since most plants are already at phenostage 3-4.
\par Britany came to meet me at 2pm to do the shoot elongation monitoring. We finished around 4, but we didn't fill in the trees with paper rulers. 

\def\day{\textit{June 20, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I started a R script to check the hobo light loggers. It took me quite some time. After, I met Britany again to finish shoot elongation logging in the excel. I also did phenomonitoring of Segi as it's the only species that has not fully leafed out. 
\par I also finished the greenhouse arrangement with the light loggers that are now included in it. 
\par In the afternoon, we had a nice lab meeting at the Botanical Garden. 

\def\day{\textit{June 21, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I worked from home this morning. I did some emails. Then I went to Totem to maintain the plants and clean around a little.
\par I modified how the comments were entered in the shoot elongation file on doy164 (moved them back to the note column)

\def\day{\textit{June 24, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Started the day with a meeting with Roman. I took some notes on the chambers that I should add to the lab git. After, I finally started a document on the notes on the climate chambers maintenance and schedule creation.
\begin {itemize}
	\item Start git issue on the tree inventory -- done
	\item Change the schedule in the CC so they are at 20C and the lights were turned down. 
	\item Email the maintenance guy for the biochambers for 2 things: clean the filters and tell him not to repair the copper pipes.  -- done
	\item Add notes to the labgit on chambers -- done
	\item contact opens lab to trouble shoot the dendrometers
\end {itemize}

\par In the afternoon, I went back to Totem so I can install 6 more temperature loggers. Lizzie came to meet me at 2:30. We discussed the project, expectations for the summer and the egret retreat. To do list for tomorrow is the things I will need to get done soon. 

\def\day{\textit{June 25, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I started the day with the creation of a new spreadsheet: miscellaneous which includes the different monitoring. Either if the apical shoot is dead, if there was chlorosis, mildew, etc. 
\par After this, I started rearranging my repo because it started to be quite messy. I also created some notes on how to use the hobo loggers. Then I wrote a blog post for the trip at RBS.
\begin {itemize}
	\item Check how much light difference there is between the loggers. Ideally, we would remove this factor from the models as it would complicate things a lot. I will talk with Fredi about this. 
	\item Email the person Lizzie recommended on the Segi physiology
	\item make a note of chlorosis monitoring and the plants that got light damage in the spring (this might not be possible anymore) -- done 
	\item Change the schedule in the CC so they are at 20C and the lights were turned down. 
\end {itemize}

In the afternoon, I got lots of things done: finalized the hobo loggers description, I reorganized my repo and I did some research on the bud set. Then I read 2 papers and made two permanent notes out of them. Lizzie stopped by and asked me to figure out which software, languages and others she could explain during the lab meeting. 

\def\day{\textit{June 26, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe+Mao}
Emailed Alana Chin. Lizzie recommended reaching out to her cause she might have information on growing sequoia. After I kept working on some notes that I started yesterday.
\par At 1 pm, I went to pick up Fredi at the airport. His flight was delayed so I returned to the office at 3 pm. Mao and I went to monitor the shoot elongation together. We didn't finish all the measurements as it was raining quite much. We'll get it done tomorrow morning. 
\par I came back to the office and worked on the script for the light hobo loggers. I want to find out if there is a big difference between the light intensity between the different blocs. 
\par I read two more papers. Took fleeting notes, but I have to make them permanent 
\def\day{\textit{June 27, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe+Mao}
Mao and I finished the shoot elongation measurements this morning. I started around 9:45.
I replied to Alana regarding the phenology of Segi and to Sally Otto for the biomathematics class in the fall. 
\par I started taking the bayesian class Lizzie recommended. Then I worked again on my script for the light hobo loggers. 
\par We had the training on wilderness at 1 pm. 

\def\day{\textit{June 28, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Started the day with a meeting with Alana Chin to discuss how should I monitor better the Se
\textbf{To do list for today}
\begin {itemize}
	\item Install Stan on R
	\item Make sure to run the script Deirdre told me to run. 8 school tutorial
	\item Finish first class of the Stats class
	\item Finish organizing the repo: Objects, greenhouse design, ordering, equipements, in the note folder. Once methods are tiped nicely, it goes in docs folder. 
contact opens lab to trouble shoot the dendrometers

