

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}
%\usepackage{cite}
\usepackage[margin=1in]{geometry}
\usepackage{array}
\usepackage{graphicx}
\usepackage{caption}
\graphicspath{ {./figures/} }
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{lineno}
\usepackage{soul}
\usepackage{xcolor}
\sethlcolor{yellow}
\linenumbers

%%%%%%%%%%%%%%%%%
\title{Thesis Proposal}
\date{\today}
\author{Christophe Rouleau-Desrochers}
\begin{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle


%<><><><><><><><><><><><><><><><><><><><>
% INTRODUCTION %
%<><><><><><><><><><><><><><><><><><><><>
\section{Introduction}
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
% SECTION 1.1. %
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\subsection{Climate change impacts on tree phenology}
An important body of research from the past decades have shown convincing evidence that human activity are increasingly affecting many worldwide environmental processes (Parmesan2003Towards; Intergovernmental2023Climate; Laurance2006Have;Ceballos2017Biological). This can be through land use change and destruction, pollution, invasive species, ressource overexploitation and climate change (Wu2013Key; Driscoll2018A biodiversity; Parmesan1999Poleward). That alone raises major concern and actions have been deployed to mitigate these impacts, with varying success (e.g. Cambell2014Producing). Even though immediate actions can have positive impacts and potentially reduce some threats to biodiversity, reversing 150 years of human induced greenhouse gas emissions is harder. These emissions have already affected Earth's climate and they are projected to continue affecting Earth's climate centuries. While there is a scientific consensus that observed climate change is human-caused (IPCCDetection, Lynas2021Greater, Oreskes2004The consensus), the magnitude and the extent of the consequences that a warming climate will have on biological processes are still debatable (Huey2012Predicting). Historically, the first case of attribution of a biological change to climate change was about poleward shifts of european butterflies in Europe in response to regional warming (Parmesan1999Poleward).

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\textbf{Trends of spring and autumn phenological events and their drivers}
The most frequently observed biological impact of climate change over the past decades are major changes on spring and autumn phenology --- the timing of recurring life history events \cite{parmesan_globally_2003,cleland_shifting_2007,lieth_phenology_1974,woolway_phenological_2021,menzel_european_2006}. Understanding the consequences of these shifts on ecosystems requires understanding how much the growing season has changed \cite{duputie_phenological_2015}. Spring phenological events (e.g. budburst and leafout) have been advancing from 0.5 \cite{wolfe_climate_2005} to 4.2 days/decade \cite{chmielewski_response_2001,fu_recent_2014} and are mainly driven by temperature \cite{chuine_why_2010,cleland_shifting_2007,penuelas_responses_2001}. In contrast, autumn phenology (e.g. budset and leaf colouring) is delayed, though to a much lesser extent than spring \cite{gallinat_autumn_2015,jeong_macroscale_2014}. The drivers regulating autumn phenology are far less understood than those of spring for many reasons. First, autumn phenology has attracted much less attention compared to spring \cite{piao_plant_2019}. Second, the data is often much noisier, since meteorological conditions in the fall can drastically influence phenological phenomena. To illustrate this, trees going through leaf senescence are subjected to a gradual leaf abscission that follows nutrient reabsorption, and the leaves within the same individual might be at different senescence stage, but a strong wind spell may trigger leaf drop for all leaves, thus affecting the temporal resolution of these data (Wu2024Canopy). However, there is a general belief that autumn phenophases are driven by shortening photoperiod and colder temperatures \cite{cooke_dynamic_2012,flynn_temperature_2018,korner_phenology_2010,delpierre_temperate_2016}. Different hypothesis are proposed to explain delayed autumn phenophases. First, warmer autumn temperature may extend the activity of photosynthetic enzymes which could be maintained at a a higher level. Thus, the degradation rate of chlorophyll would decrease and timing of senescence would be delayed (Yan2021Divergent). Second, summer droughts could make trees pause their activity schedule and delay senescence to increase carbon assimilation (Dox2022Severe). Third, there could be an antagonistic effect of warming and brightening---caused by reductions in atmospheric pollution and cloud cover (Sanchez2015Reassessment)---on leaf senescence (Wu2021Atmospheric). Brightening accelerates the leaf senescence processes and reduces the temperature sensitivity during that period, counteracting the expected warming-induced delays in leaf senescence. The photo-protection and sink limitation hypothesis provide plausible explanations for the negative effect of radiation on leaf senescence and the declining effect of temperature sensitivity of leaf senescence in response to brightening (Wu2021Atmospheric; Zani2020Increased). \\

% DO THIS: REVISE THE LAST SENTENCE OF THE ABOVE PARAGRAPH
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\textbf{1.1.Mis-leading evidence of declining sensitivity to warming}
% this section needs some heavy work!
While we have convincing proof that spring events advanced in the past decades, there is evidence that this might decelerate because of declining sensitivity to warming (Fu2015Declining; Meng2020Urban). The proposed mechanism is through the action of warmer winters on tree dormancy. In the fall, trees in boreal and temperate forests slowly enter dormancy which is initiated with budset. During this phases, cold hardiness increases which prepares the trees for the upcoming cold temperatures and prevents tissue damage. Then, the trees enter dormancy, during which a certain duration of chilling temperatures---with some interaction with photoperiod for some species---is necessary for the trees to be ready to accumulate forcing (Vitasse2014TheInteraction). In the late winter and early spring, they go through two forms of deacclimation before budburst (Vitasse2014TheInteraction). When deacclimation is reached, a certain amount of heat (forcing) is required to initiate budburst (Fu2015Declining). The argument of declining sensitivity appears here: heat requirement is met sooner in warm springs, but it's also negatively correlated with chilling (Yongshuo2015Declining). However, it is this interaction between chilling and forcing requirements that determines the timing of leaf unfolding. In other words, a decrease in chilling accumulation is proposed to explain the observed weaker spring temperature sensitivities, where spring forcing looses of its relative importance (Fu2015Declining; Meng2020Urban; Wolkovich2021ASimple). However, a meta-analysis compiling 72 studies of 203 species suggests that declining sensitivities observed in Europe may be a statistical artifact of how these responses are calculated, thus casting doubt on this proposed trend (Ettinger2020Winter). This statistical artifact may be caused by using linear models for calculating non-linear processes (Wolkovich2021Asimple).

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\textbf{1.2.Mechanisms that could limit growth despite having a longer growing season}
Plants seasonal activity has internal and external controls, both determined by environmental conditions. Internal controls operate via autonomous clocks, activating genes and releasing hormones which often relly on chilling and/or photoperiod. The external controls, often refered to as forcing, act directly on the developmental rate, meristem activity, tissue differentiation and metabolism (Korner2023Four). These controls have often been overlooked, but are neverteless critical to our understanding of plant's capacity to adjust their activity schedule in response to changing conditions (REF). In lights of this, I hypothesize two possible drivers that could explain why a longer growing season might not lead to increased growth: external (environmental) \cite{kolar_response_2016} and internal (via physiological constraints)\cite{zohner_effect_2023} constraints to growth. 

\textit{1.2.1.External constraints}
The complex nature of climate change makes predicting the external limits to growth hard to quantify at the individual level, as these drivers affect communities as a whole. However, drought, spring frost and heat waves are commonly mentioned as the main extreme events that could limit tree growth under climate change \cite{tyree_xylem_2002, choat_triggers_2018, li_widespread_2023,trenberth_global_2014,intergovernmental_panel_on_climate_change_detection_2014,chiang_evidence_2021,polgar_leafout_2011,reinmann_compensatory_2023}. Their respective mechanisms, global trend of occurence, consequences and difference among species are describe in Tables ***. \\

\textit{1.2.2.Internal constraints}
As for the internal constraints to growth, recent hypothesis propose that broadleaf deciduous tree species may be sink-saturated, such that longer growing season with more carbon fixation do not necessarily increase growth (Dow2022). This one pathway is directly linked to the internal controls of plant growth, which are under strong genetic control. Many studies showed, that in addition to height and radial growth varying across species, these growth responses also vary by site (REF). Populations from higher altitude or latitude grow less under the same conditions than individuals from lower altitude or latitude. This is further suported by phenological studies showing that growth end arrives earlier from populations of higher latitude, demonstrating local adaptation to potentially avoid fall frost, before nutrient uptake has finished. These trees rely on photoperiod cues for setting buds (stopping height growth) (WolkovichUnpublishedWhy). 
% Maybe go towards carbon fertilization: This goes against a long-standing, but recently debunked paradigm of growth stimulated by carbon fertilization (Jiang2020TheFate (notinzotero). 

Growth seasonality has huge consequences on overall annual growth and so are the environemental conditions during these periods. For instance, warming spring temperatures seem to positively affect growth, but recent evidence suggest a shift in this net positive effect near the summer solstice. Indeed Zohner 2023 found that warmer temperatures before the solstice advanced the onset of senescence, but it slowed the progression of leaf colouring when temperatures postsolstice were warmer. This further reinforces the importance of understanding how the timing of warmer conditions affect tree species. \\ % work on that closing sentence, which could be moved elsewhere.

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\textbf{How these shifts translate into effects on trees/forests are not clear}
Shifts in spring and autumn phenology support a long-lasting and intuitive assumption that earlier spring and delayed autumn events lead to longer seasons---and thus increased growth \cite{keenan_net_2014} (Stridbeck2022Partly). However, research from the past three years has cast doubt on this hypothesis \cite{dow_warm_2022,green_limits_2022,silvestro_longer_2023}. For instance, Dow \textit{et al}. (2022) showed that despite an earlier growth onset, neither growth rate nor overall annual increment was increased by longer seasons. This could substantially affect carbon-cycle model projections and thus feedbacks to future climate \cite{richardson_climate_2013,swidrak_comparing_2013}. 

Understanding these findings requires answering why trees do not grow more despite longer growing seasons (REF). While carbon allocation to above ground biomass is one of the largest carbon sink, how this carbon is allocated into wood is pooly understood. Indeed, the linear relationship assumption between wood growth and carbon assimilation is not well supported mechanisticaly and represents an important limitation of vegetation models (Cabon2022). NPP represents the difference between photosynthesis and plant respiration, but this commonly used metric completely omits the representation of growth processes. This is perhaps because of a long-lasting paradigm of source-limited photosynthesis. This has now since then been debunked with carbon fertilization experiments, supporting evidence that direct environnemental constraints on growth may be stronger than those on photosynthesis (Friend2019On; Parent2010Modelling). This opens up a new, poorly tested, temperature sensitivity between cambial activity and photosynthesis. Growing evidecence suggest that cambial activity may be more sensititive than photosynthesis to a range of environmental conditions such as: water and nutrient availability, and temperature (Cabon2022; and others cited in there**). This demonstrates that carbon projection models that heavily rely on vegetation alone may mislead the amount of carbon sequestrated in our forests. 

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\textbf{Growing season shifts and consequences on forest ecosystems and services}
Spring and fall phenological events are shifting with debatable consequences on tree growth. The sensitivity of cambial activity to water, temperature and nutrients have the potential to have far-reaching consequences given the hard-to-predict nature of future climate change, where any of these variables have the potential to vary with high amplitude (REF). This expected assymetry of future environmental changes makes understanding the internal and external limits to growth critical. Especially, the capacity to tease appart different biomes---as for example boreal vs tropical forests are expected to react differently---is critical and empirical data coming from experiments, but also from observations are paramount to predict the changes of forest carbon offset from human GHG emissions.  

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
% SECTION 1.2 %
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\subsection{Nature of the problem, and how to address it}

\textbf{1.2.1. Past phenological trends can help (or not) predict future phenological changes}
Observed phenological trends in the last decades cannot be used directly to extrapolate future phenological changes because: (1) the mechanisms guiding them aren't clear and (2) phenological responses of trees to warming are very likely to not be linear (Fu2013Sensitivity; Ettinger2020Winter). Indeed, accurate predictions require an in-depth accurate mechanistic understanding of phenophases and their sensitivities to environmental drivers, especially to temperature and photoperiod (Fu2013Sensitivity). Therefore, the very foundation of the assumption that longer seasons increase growth may shift with future climate change. The well observed advance in spring phenology may slow down and delayed fall phenology may shift towards earlier leaf senescence (through summer drought induced growth cessation).

Variation is extreme when examined across species (Wolkovich et al., 2014), but additional variation can be seen within species over space (Vitasse et al., 2013; Kramer et al., 2017) and time (Yu et al., 2010; Fu et al., 2015). 

\textbf{1.2.2. The assumption that longer seasons lead to increased growth is called into question}
Recent work shows an absence of increased growth despite apparent better environmental conditions, thus casting doubt on a simple and intuitive positive relationship between growing season length and growth. This paradox further emphasizes that we need to understand better the drivers regulating growth across biomes, but also how these drivers vary accross the species within these biomes. Phenology vary greatly across species (e.g. closely related species tend to budburst at similar time under similar conditions) (Wolkovich2013Progress), but so does the relationship between growth and season length which may explain the wide variation of this relationship among communities (Buckley2012Functional). This highlights a weekness of certain carbon sequestration models that pool species together, which likely overpass important that nuances in the growth responses that could be explained by species differences. This may mislead the future of forest carbon source-sink ratios \cite{green_limits_2022,cabon_cross-biome_2022}. To better understand how different species respond to warming, different strategies can be used. Experiments are paramount to robustly tease apart the external vs internal drivers (e.g. warmer springs from severe drought later in the season---a common co-occurring reality in natural environments) \cite{morin_changes_2010,primack_observations_2015}. However, experiments are most often performed on juvenile trees, which are critical for their role in forest regeneration projections, but their responses can hardly be translated to mature trees, which hold the overwhelming carbon biomass proportion of forests \cite{augspurger_differences_2003,silvestro_longer_2023,vitasse_ontogenic_2013}. Leaf phenology through ground-based observations can provide valuable insights into the growth onset and end of trees that are not suitable for experimental trials since cambial and leaf phenology are closely linked to another. It is to say that knowing when leaves elongate and color, can guide when trees start and stop to grow---fundamental metrics to determine the growing season length. Ground observations has the advantage of providing accurate data of phenological events for specific sites and species. Recently, the widespread use of smart-phones has opened a whole new world of possible phenological through citizen scientitists records of data over much larger areas and for a wider range of species (Piao2019, Dickinson2012, Hufkens2019). While there are drawbacks of these observations (e.g. non-standard protocols, highly uneven spatial-temporal distribution of these observations), these methods have a huge potential to diversify the phenology data. % these few lines shouldn't go here. 

\textbf{1.2.3. Impacts on carbon source-sink projections} 
% ask Lizzie: should I skip this because I mention it above?
% below might not be relevant here
%Atmospheric dryness characterised as the difference between the actual water vapour pressure and the saturation water vapour pressur is often measured through the proxy of vapor deficit pressure (VPD) has been increasing (Yuan2019Increased*;Yuan2025Impacts) and is projected to keep increasing under continuous anthropogenic forcing (Fang2022Globally*).

\textbf{1.2.4. Goals of my thesis} 
Using citizen science data, a common garden trial an a large-scale experiment, I aim to better understand how different tree species, at different lifespan stages vary in their growth responses to different season length. 

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
% SECTION 1.3. %
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\subsection{Complexity of measuring growth and defining growing season length}
\textit{What is a growing season?} \\
% ask Lizzie if the paragraphs below make any sense
To understand how trees respond to growing season conditions, it is important to define the growing season and growth.
First, a problem that arises when one tries to quantify how shifting growing seasons affect growth comes from the definition of the growing season itself. Recently, Korner 2023 proposed four definitions adressing this issue: 1. true growing season, based on measurable growth; 2. phenological season, based on visible phenological markers; 3. the productive season, based on primary production and 4. meteorological season, based on environmental conditions.

Here, I will focus on how definition 2., incorporating 4. affects definition 1. as the data collected for this thesis can't adress 3. I will use definition 2. to infer a "window of opportunity" during which meteorological conditions (4.) will be used to calculate growing degree days (GDD). I am using the meteorological season within a contrained window, instead of simply using it irrespective of phenology because of the illusion that an absolute increase in GDD over the last decades---irrespective of the timing of phenophases---also increases growth. Springs are warmer, falls are also sometimes warmer, and summers are warmer which together, increase the number of GDD which may appear to be a reliable proxy for better environmental conditions. However, a fundamental distinction is that there is a "theoritical" and a "real" period at which trees can grow, which is usually defined through the period between budburst and leaf senesence, highlighting the importance of accurate phenology data (REF).

Models using degree-days are increasing even though they have been used for decades in agriculture (McMaster1997Growing, REF). These rely on developmental patterns that are based on temperature dependance to estimate a particular ecological process, in my case, tree-ring width. These models describe a particular response variable as a composite of time and temperature as opposed to time alone. This is a partimonious method that requires three variables: daily minimum and maximum temperatures and the base temperature at which the process of interest cannot occur (cambial activation in this case) (McMaster1997Growing-degree;Moore2014Developmental).  Though this simplicity comes with a drawback of over-simplifying potentially complex developmental processes in response to varying environemental conditions within a season (Bonhomme2000Bases).

\textit{What is growth?} \\ 
What is growth? Wood formation (xylogenesis) is the major biological process by which carbon is allocated and long-term stored in woody plants. Radial growth is determined by the production of xylem and phloem cells that begins with cambial activation and cell production by cambial initials, following by cell differentiation through the following events: 1. Cell enlargement 2. Secondary-wall formation and lignification and 3.programmed cell death (Silvestro2025From;Etzold2021Number). The rate and duration of these phases lead irreversible radial growth increment usually represented through tree-rings. In these, secondary xylem cells account disproportionally to the number of cells produced because they divide more than phloem cells (Rathgeber2016Biological; Plomion2001Wood). \\

\textbf{1.3.1. Traditional diameter measurements miss the resolution of annual growth increment} \\
Foresters have measured tree diameter and height for decades to infer allometries that could give them a good estimate of how much wood they could collect in a forest (e.g. Meyer1940A Mathematical; Saunders2007Height). The widely used method in forestry is to measure diameter at breast height (DBH) at punctual time intervals (REF). However these measurements don't provide short-term indicators of growth---especially if taken at multiple years intervals. Therefore, extreme events affecting growth are likely to be missed. In addition, many forest inventories only report diameter measurements and exclude height, because of logistical contraints (Saunders2007Height), which reduces biomass estimation quality. This growth data lacks the temporal resolution necessary to properly infer a relationship between growth and environmental conditions. 

Alongside diameter-height allometric relationship, dendrochronology and its related fields also have long standing traditions in forestry and sylviculture. Indeed, tree-ring research was developped in the early 1900s to perform archeaelogical dating and climate reconstruction (Pear2020New and e.g. Douglass1928). Since then, different dendrochronology methods have developped for different purposes, such as the calibration of the terrestrial radiocarbon curve (Helama2023Type;Reimer et al., 2020) and modelling Earth's past climate and ecological change (REF). More recently, dendroecology---applications of dendrochronological techniques to problems in ecology---emerged to answer ecological problems as well as to hindcast (e.g. Bergeron2004Fire) and forecast ecological processes both at the regional (Gazol2017Forest) and global scale (Manzanedo2019Towards;Büntgen2018). Now, these methods can be used to understand more precise growth patterns and their relationship with different environmental factors.\\

\textbf{1.3.2. Growth increment needs to incorporate wood density in order to evaluate how much structural carbohydrates were stored within a single year.}
While tree-ring width are reliable proxies to how much trees grow in each year, at relatively low cost and time, the inclusion of wood density in the analysis may provide data hidden within the tree rings. Indeed Cufar 2008 (Cufar2008Tree-ring) showed that intra- and inter- annual density variations in beech provided more information and at a higher temporal resolution than tree-rings widths alone. 

In addition to densitometry, increasing number of studies are going beyond traditional ring width by performing analysis using wood anatomy data. For instance, low cost techniques (e.g. "blue intensity" proxy for latewood desity (Babst2016Blue*, Campbell2007Blue*) and high resolution imaging (von Arx G 2014Roxas; SkippyWSL)) give rise to a whole new world of possibility regarding the microscopic components of wood anatomical features. Micro-anatomical analyses within tree-rings could be applied to a wide range of applications (Pearl2020New). HERERThe character of annual rings, cell structure, timing of growth and markers for trauma can assist in answering a variety ecological and physiological questions previously unanswered with ring width or density alone, such as how growth is affected by growing season length under anthropogenic forcing.

\textbf{1.3.3. Asynchrony between primary and secondary growth (internal growth control?}
I argue that internal growth control in trees may shape their growth responses to growing season length and these can be split into two categories: primary and secondary growth synchronicity and growth determinancy. 

Primary (shoot) and secondary (xylem and phloem formation) growth both contribute to how much carbon is stored in plant tissue, but how much they differ in their responses to environmental drivers is poorly understood. After a dormancy period, trees will start growing, both vertically (primary) and horizontally (secondary), but there is extreme variation among species as to when each growth starts, for how long it lasts and when it stops. For instance, ring-porous speceis intiate primary growth early in the season, sometimes, even before budburst (e.g. oaks) (Stridbeck2022Partly), whereas xylogenesis in diffuse-porour species are usually more synchronized with budburst. These two examples highlight how more complicated it might be to infer general conclusions as to how growing season shifts may also shift growth, where some species may extend their primary growth, but restrict their secondary growth and vice versa.

In addition to differences in primary and secondary growth synchronicity, the role of internal growth control---genetically controlled developmental program where overlooked growth determinancy may mishape our understanding of growth responses to growing season length. In perrenial plants, two dichotomous growth strategies are commonly mentioned: determinate and indeterminate growth, though it may appear as species may exist along a gradient of these. Indeterminate growth is usually associated with short-lived and fast growth species where these life-history strategies may give them a competing advantage as tissue growth can be produced quickly in response to changing environmental conditions, but this comes with higher risk of late spring and early fall frost as well as late droughts. At the opposite side of the spectrum, determinate species are usually long-lived and slow-growth and are mainly constrained by conditions during bud formation, this may increase bud survival at the detriment of opportunistic growth in face of better-than-expected conditions. 

Thus, these characteristics, that greatly vary across species lead make hard the growth pattern predictions of species to shifting growing season length.% shitty sentence that I should either remove or change a lot

\textbf{1.3.4. Getting growth temporal resolution is labor-intensive and expensive (e.g. dendrometer costs)}
To know when trees start and stop to grow within a single growing season (data not extractable through tree-rings), there are two methods, one being labor intensive and the other being expensive. 

1. Trephor allows recurent sampling of mature trees where a 2mm microcore is extracted from the tree a different times during the growing season. By sampling multiple times a single tree, growth temporality can be infered by counting the ring cell increment between each sample. While this non-detrustive tool can be extremely valuable, getting large sample size can hardly be feasible. 

2. Dendrometers allow to monitor stem radius variation, measuring irreversible secondary growth, but aslo stem water fluctuations and thermal expansion, often leading to biased estimates of growth increment temporality (Camarero2009Plastic).

% talk here about intra-annual density fluctuation: https://brill.com/view/journals/iawa/37/2/article-p232_8.xml


% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
% SECTION 1.4. %
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\subsection{Objectives} 

% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
% SECTION 1.5. %
% <><><><><><><><><><><><><><><><><><><><><><><><><><><><><><>
\subsection {Research questions} 

\textbf{1.4.1. Fuelinex}

\textbf{1.4.2. CookieSpotters}

% PLACE SOMEWHERE ELSE
%Thus, I propose to use a combination of one experiment to test internal (Chapter 1) limits to growth along with two observational studies (Chapter 2). This will allow me to address the paradox of the absence of increased growth despite apparently improved growing season conditions. 

\section{Methods}

%For stats for fuelinex, look up this note in the slipbox: Importance of robust statistics to tease cues apart

% ============================
% 1. CC  X Phenology
% ============================
% --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
% Tables spring frost, drought and heat waves $
% --- --- --- --- --- --- --- --- --- --- --- --- --- --- --- ---
		\textbf{3.1. Spring frosts} \\ %emwJuly1 -- Wow, Christophe! This is super impressive and the notes and refs generally align with my view of the literature (though I think you could find other refs beyond Chiang that say it's other parts of the world, but overall this is very good). I would consider keeping this for your introduction chapter for sure, just be careful to not try to write all of this out for the reader  early in the intro as it will be too specific too fast, but this is great!
\resizebox{\textwidth}{!}{
\begin{tabular}{|>{\raggedright\arraybackslash}p{4cm}|p{12cm}|}
\hline
\textbf{} & \multicolumn{1}{c|}{\textbf{}} \\
\hline

\textbf{Mechanisms} & Early warm spells $\rightarrow$ early leaf out $\rightarrow$ hard frost ($<$-2Celsius) $\rightarrow$ tissue death = loss of photosynthetic capacity \cite{polgar_leafout_2011}; Response: second cohort of leaves are more efficient and mitigate carbon sequestration loss \cite{reinmann_compensatory_2023} \\
\hline
\textbf{Global trend of occurrence} & Most vulnerable regions are the ones with no past risk of occurrence (); $\uparrow$ in Europe and East Asia, but $\downarrow$ North America; Global trend is controversial \cite{reinmann_compensatory_2023} \\
\hline
\textbf{Consequences (Individual and Ecosystem level consequences)} & Loss of vegetative tissue = $\downarrow$ photosynthesis = $\downarrow$ and remobilization of NSC to repair damaged tissues = $\downarrow$ secondary growth (Meyer24); Loss of reproductive tissue (higher flower mortality) (REF); Costs for orchards and stuff \cite{reinmann_compensatory_2023} \\
\hline
\textbf{Differences across species/provenance} & \\
\hline
\end{tabular}
} 

\clearpage
	\textbf{3.2. Drought} \\
\resizebox{\textwidth}{!}{
\begin{tabular}{|>{\raggedright\arraybackslash}p{4cm}|p{12cm}|}
\hline
\textbf{} & \multicolumn{1}{c|}{\textbf{}} \\
\hline
\textbf{Mechanisms} & — Hot temperature + low precipitation (aka global-change-type drought \cite{tyree_xylem_2002})= $\uparrow$ evapotranspiration$\rightarrow$ less water in soil $\rightarrow$ cavitation $\rightarrow$ embolism $\rightarrow$ hydraulic failure \cite{tyree_xylem_2002} = tissue death \citep{choat_triggers_2018}; 

— Earlier spring phenology = longer GS $\rightarrow$ increases vegetative growth $\rightarrow$ increases evapotranspiration $\rightarrow$ increases drawdown of soil moisture = progressive water stress \cite{li_widespread_2023}

— Long-term vs short-term stomatal responses and consequences on tissue death \citep{choat_triggers_2018}; 

— Recovery and its determinants \citep{choat_triggers_2018,li_widespread_2023}\\
\hline
\textbf{Global trend of occurrence} & — $\uparrow$ precipitation anomalies since 1990 \cite{trenberth_global_2014};  

— Models often exclude PDO/ENSO which limit the capacity to attribute increasing droughts to CC  \cite{trenberth_global_2014}; 

— Weak evidence of detection and attribution of changes in meteorological drought since the mid-20th century \cite{intergovernmental_panel_on_climate_change_detection_2014}; 

— Using a spacial, model-based perspective, anthropogenic forcing increased the frequency, duration and intensity of SPI-based droughts for Americas, Mediterreanean, W/S Africa and E Asia \cite{chiang_evidence_2021} \\
\hline
\textbf{Consequences (Individual and Ecosystem level consequences)} & — Recurring droughts may limit trees' ability to recover from other types of stress.

—Tree mortality (e.g. Texas and California extreme droughts are estimated to have killed 300 and 102 million trees \cite{li_widespread_2023})\\ %emwJuly1 e.g. is always lowercase
\hline
\textbf{Differences across species/provenance} &  \\
\hline
\end{tabular}
} \\
\par

\textbf{3.3. Heat waves : \textit{needs to be filled}}\\
\resizebox{\textwidth}{!}{
\begin{tabular}{|>{\raggedright\arraybackslash}p{4cm}|p{12cm}|}
\hline
\textbf{} & \multicolumn{1}{c|}{\textbf{}} \\
\hline
\textbf{Definition:} &  Heat wave is a period of excessively hot weather (5 or more consecutive days of prolonged heat in which the daily maximum temperature is higher than the average maximum temperature by 5 °C ), which may be accompanied by high humidity (Marx2021Heat) \\
\hline
\textbf{Mechanisms} &  $\uparrow$ atmospheric CO2 = $\uparrow$ temperature $\rightarrow$ $\uparrow$ heat waves... More specifically: A mechanism for the increase occurence of heat waves is a weakeking of the polar jet stream (important weather factor for middle latitude regions of North America, Europe and Asia) caused by global warming which increases the occurence of stationnary weather, resulting in heavy rain falls or heat waves(Marx2021Heat).  Extreme heat $\rightarrow$ growth either through (1) Directly via cell processes disruption or (2) indirectly via effects of rising leaf-to-air vaport deficit (VPD) (Gagne2020Limited).

Increased temperature leads to reduced photosynthesis which can be attributed to: 
1. Damage to photosynthetic machinery
2. Inactivation of RUBISCO
3. Reduction to RuBP regeneration
4. Membrane stability (Markus2025Heat)
5. Increased mitochondrial respiration and photorespiration
\\
\hline
\textbf{Global trend of occurrence} & Heat waves have increased (Meehl2004More;Gagne2020Limited; Teskey2015Responses) and are expected to increase under future climate change (Yao2013Comparison;Teskey2015Responses; Dosio2018Extreme;IPCC2014). Summertime extreme temperatures associated with prolonged heat waves, lasting for several weeks, now impact approximately 10\% of land surfaces, up from only 1\% in the 1960s. (Teskey2015Responses).
The more intense and more frequently occurring heat waves cannot be explained solely by natural climate variations and without human-made climate change (Marx2021Heat).
 \\

\hline
\textbf{Consequences (Individual and Ecosystem level consequences)} &  - Reduced photosynthesis (Gagne2020Limited) - Increased mortality - Photosynthetic tissue loss \\ 
\hline
\textbf{Differences across species/provenance} & Some species have thermal photosynthetic/respiratory acclimatation while others don't. Growth and survival will change depending on species to thermally acclimate to both photosynthesis and respiration 
- This is explained by growth strategies of gymnosperms vs angiosperms (which are usually better)
 \\
\hline
\end{tabular}
}


\subsection{Climate change impacts on tree phenology} 
Climate change impacts on biological systems and how phenological trends are already shifting with warming temperatures. 

%%%
\begin{table}[p]
\centering
\caption{Fuelinex species grouped by tree type, life history, and wood anatomy.}
\begin{tabular}{|>{\raggedright\arraybackslash}p{7cm}|p{5cm}|p{3cm}|p{1cm}|}
\hline
\multicolumn{4}{|c|}{\textbf{Deciduous Trees}} \\
\hline
\textbf{Common Name (Latin)} & \textbf{Life History Strategy} & \textbf{Wood Anatomy} & \textbf{n (approx)} \\
\hline
Bur oak (\textit{Quercus macrocarpa}) & Slow-growth, long life & Ring-porous & 87\\
Bitter cherry (\textit{Prunus virginiana}) & Fast-growth, short life & Diffuse-porous & 78\\
Box elder (\textit{Acer negundo}) & Fast-growth, short life  & Diffuse-porous & 90\\
Balsam poplar (\textit{Populus balsamifera}) & Fast-growth, short life  & Diffuse-porous &84 \\
Paper birch (\textit{Betula papyrifera}) & Fast-growth, short life  & Diffuse-porous &90\\
\hline
\multicolumn{4}{|c|}{\textbf{Evergreen Trees}} \\
\hline
White pine (\textit{Pinus strobus}) & Slow-growth, long life & & 89\\
Giant Sequoia (\textit{Sequoiadendron giganteum}) & Slow-growth, long life & & 54\\
\hline
\end{tabular}
\end{table}
%%%
% ============================
% Wildchrokie
% ============================
\subsection{Wildchrokie}
\begin {enumerate}
	\item Common garden from 2015 to 2023
	\item Four species within the Betulacea family (Table 2)
%%%
\begin{table}[p]
\centering
\caption{Wilchrokie species grouped by tree type, life history, and wood anatomy.}
\begin{tabular}{|>{\raggedright\arraybackslash}p{7cm}|p{5cm}|p{3cm}|p{1cm}|}
\hline
\multicolumn{4}{|c|}{\textbf{Deciduous Trees}} \\
\hline
\textbf{Common Name (Latin)} & \textbf{Life History Strategy} & \textbf{Wood Anatomy} & \textbf{n} \\
\hline
Paper birch (\textit{Betula papyrifera}) & Fast-growth, short life  & Diffuse-porous & 8\\
Yellow birch (\textit{Betula alleghaniensis}) & Moderate-growth, moderate life & Diffuse-porous & 21\\
Grey birch (\textit{Betula populifolia}) & Fast-growth, short life & Diffuse-porous & 29\\
Grey alder (\textit{Alnus incana}) & Fast-growth, short life & Diffuse-porous & 31\\
\hline
\end{tabular}
\end{table}
%%%
	\item Data: phenology, height, tree rings
	\item Analysis: Hierarchical model to understand how tree ring width relates to GDD
\end {enumerate}

% ============================
% Treespotters
% ============================
\subsection{Treespotters}
\begin {enumerate}
	\item Citizen science project from 2015 to today (Table 3)
\begin{table}[h]
\centering
\caption{Treespotters species grouped by tree type, life history, and wood anatomy.}
\begin{tabular}{|>{\raggedright\arraybackslash}p{7cm}|p{5cm}|p{3cm}|p{1cm}|}
\hline
\multicolumn{4}{|c|}{\textbf{Deciduous Trees}} \\
\hline
\textbf{Common Name (Latin)} & \textbf{Life History Strategy} & \textbf{Wood Anatomy} & \textbf{n} \\
\hline
American basswood (\textit{Tilia americana}) & Fast-growth, moderate life & Diffuse-porous & 5\\
Eastern cottonwood (\textit{Populus deltoides}) & Fast-growth, short life & Diffuse-porous & 4\\
Northern red oak (\textit{Quercus rubra}) & Moderate-growth, long life & Ring-porous & 4\\
White oak (\textit{Quercus alba}) & Slow-growth, long life & Ring-porous & 5\\
Pignut hickory (\textit{Carya glabra}) & Slow-growth, long life & Ring-porous & 4\\
Shagbark hickory (\textit{Carya ovata}) & Slow-growth, long life & Ring-porous & 4\\
River birch (\textit{Betula nigra}) & Fast-growth, short life & Diffuse-porous & 5\\
Yellow birch (\textit{Betula alleghaniensis}) & Moderate-growth, moderate life & Diffuse-porous & 4\\
Sugar maple (\textit{Acer saccharum}) & Slow-growth, long life & Diffuse-porous & 5\\
Red maple (\textit{Acer rubrum}) & Slow-growth, long life & Diffuse-porous & 4\\
Yellow buckeye (\textit{Aesculus flava}) & Moderate-growth, moderate life & Diffuse-porous & 5\\
\hline
\end{tabular}
\end{table}

	\item Tree coring
	\item Data: phenology, tree rings
	\item Analysis: Hierarchical model to understand how tree ring width relates to GDD	
\end {enumerate}


\section {References}
\bibliography{Exported_Items.bib}
\bibliographystyle{nature} % set citation style 


% old text
%\section*{Chapter 2.1. Wildchrokie: Phenological observations coupling with tree-ring width measurements for a 6-year common garden experiment} While the assumption that a longer growing season leads to increased growth is an intuitive and common one, recent evidence shows that this may not be the case. 
%How phenological season length relates to growth. This is a major question in fundamental biology, but also critical to forecasts of climate change itself, since most carbon models assume that plants experiencing longer seasons will sequester more carbon, but recent studies have called this assumption into question.


% ============================
% 2. Tree-ring stuff 
% ============================
%\subsection{Tree rings measurements as a proxy for growth}
%Using tree ring data to investigate the relationship between phenology and growth

%\begin{enumerate}
% 1)
%	\item Triggers and mechanisms behind growth onset, duration and rate.
%Growth onset and duration vary because of inter-annual differences in weather, with cambium reactivation in spring being highly dependent on temperature. 
% 2)
%	\item How radial growth is influenced by extreme weather events and their timing. 
%Growh rate increased by temperature, depends on \textbf{when} it is warmer. 
% Include in main text: Long seasons at low temperature will produce fewer cell rows than at warmer temperature.
% 3) 
%	\item Which is more important? How fast does a tree grow, or how long does it grow for?
%how growth rate may have a more direct influence on tree growth than the growing season length. 
% 4)
%	\item Methods to measure tree growth and why using tree ring images may better capture tree growth response than traditional diameter and height measurements.
% Include in main text: Diameter and height measurements are widely used to assess yearly biomass increment. However, these measurements are punctual and are often the cumulative result of many climatic events and constraints that occur during a tree's lifespan
%\end{enumerate}



\end{document}
