\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{April 1st, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{April 2, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 3, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 4, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe+Mao + Britany}
\par 
\textbf {Task}: Rotate pots
\par 
\textbf {Results}: We rotated pots from bottom to top and randomly put the pots in. We also watered the plants
\par
\textbf {Comments}: Christophe met with Lizzie over Zoom. She asked for pheno observations. I followed up with Mao who told me that budburst has already happened...

\def\day{\textit{April 5, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Mao}
\par 
\textbf {Task}: Charge dendrometers
\par
\textbf {Comments}: from 5 to 7 April

\def\day{\textit{April 8, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 9, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 10, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre}
\par 
\textbf {Task}: Started planning phenology observations
\par 
\textbf {Reasons}: 
\par 
\textbf {Results}: Visited greenhouse and growth chambers, Deirdre added to repo
\par 
\textbf {Comments}:

\def\day{\textit{April 11, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre+Justin}
\par 
\textbf {Task}:Started obs. phenology
\par 
\textbf {Reasons}: Budburst well underway
\par 
\textbf {Results}: First day of phenology observations, started with growth chamber (cool spring) as they were not as far along (more likely to get budburst). Also rotated and watered plants. 
\par 
\textbf {Comments}: Unclear how bb defined: started obs for main stem buds unless dead. Most often all buds were in similar stages. Segi---unclear what an open bud looks like. Decided just swollen and took photos. 

\def\day{\textit{April 12, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre}
\par 
\textbf {Results}: Phenology obs of greenhouse blocks, watered 

\def\day{\textit{April 15, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre}
\par 
\textbf {Task}: Observations of plants in growth chambers and greenhouse
\par 
\textbf {Reasons}: 
\par 
\textbf {Results}:Phenology obs of all plants, rolled the plastic sheds in the greenhouse. Put top layer of plants into new growth chambers
\par 
\textbf {Comments}:

\def\day{\textit{April 16, 2024}} 
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 17, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 18, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre}
\par 
\textbf {Task}: Observations of growth chambers and greenhouse
\par 
\textbf {Reasons}: Short on time today
\par 
\textbf {Results}: Observations of plants in the growth chambers and greenhouse + watered and rotated most of the plants---except last two chambers east side cage room
\par 
\textbf {Comments}: Looked into Sequoia color---found some information suggesting that the dark red/brown colour is due to cold. Should turn green when warm. I would have thought it warm enough at this point.

\def\day{\textit{April 19, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 22, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Mao+Deirdre}
\par 
\textbf {Task}: Observations of growth chambers and greenhouse
\par 
\textbf {Results}:Observations of plants in the growth chambers and greenhouse. Move some pots in the walk-in chamber to the other chambers with empty space.
\par 
\textbf {Comments}: Alru looks pretty sad.

\def\day{\textit{April 23, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 24, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 25, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Deirdre + Mao + Justin}
\par 
\textbf {Task}: Observations of growth chambers and greenhouse. Rotated growth chambers. Installed irrigation
\par 
\textbf {Results}: Greenhouse observations: Found some buds at the base of the Acma that were actually alive, but some buried in soil. Quma and Pist budburst much further alone. Seqi still looks the same. Growth chamber phenology not as advanced for Quma but started. Irrigation lines set up and we moved pots to put picks in where possible.
\par 
\textbf {Comments}: One of the chambers smells terrible and is not draining properly. Water coming out from bottom, but not out of the pipe. Maybe clogged? Maybe broken? Opened vent to help it dry out and tried to lift floor but was not able to do so to see underneath. Betpap have gotten very tall for the pots---falling over in the greenhouse, roots coming out in some of the growth chamber pots

\def\day{\textit{April 26, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 29, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Mao + Justin + Ken}
\par 
\textbf {Task}: Observations of growth chambers and greenhouse.
\par 
\textbf {Reasons}: 
\par 
\textbf {Results}: Observations of plants in the growth chambers and greenhouse.
\par 
\textbf {Comments}: Most Alru looks pretty dead, even for those leaved out already.


