`\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{June 3, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Started the day by answering many emails. I answered the git issue on nutrient depletion which took my quite some time. I also finished installing the dendrometer. I did this just so I can check if they are all working.
Met with Mao at 3:30pm to discuss worklearn. We updated the offer and will send to Lizzie to confirm the info with her. 
I checked in with Dan regarding mildew on the Acne. They don't look great right now. He told me it can take up to a week before we see any improvement. Also, I thought we had the same problem with Prvi, but its just residu of the fongicide on their leaves. 

\def\day{\textit{June 4, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Everyone from the lab}
Reifel Bird Sanctuary retreat. When we arrived, it was raining a bit, but it slowed down after 15 minutes. It was very quiet. Justin will do a slideshow of the pictures that were taken. I started working for real at 3pm. I added 2 notes to my slipbox! It was on the paper Fredi shared in git issue 14 about how to define stress in plants. I still need to cross-reference those. After this, I replied to a couple of emails that Lizzie and Christine sent me about my expense report. It took me about an hour to get this done. 

\def\day{\textit{June 5, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I went to get the Subaru serviced. I also filled up the gas tank. While I was waiting, I finished what Christine told me to do to get my expense report done. I also registered to my classes in the fall. I talked to Deirdre on my way back to talk about my talk with Christine which was very difficult. We had an idea of getting a list of things over the course of the summer of things that Deirdre should teach us.
TO DO TODAY
\begin{itemize}
    \item Scan the receipts from yesterday (dominos and rbs) -- done 
    \item Scan the receipts from today (Chevron and Kon auto) -- done
    \item Go back downstairs to grab the ziplock in the Xterra with the maintenance. Add maintenance to Git? -- done 
    \item Start a list of things Deirdre should pass on to us. -- done 
\end{itemize}

\def\day{\textit{June 6, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Lizzie and I met over Zoom in the morning to discuss many things. Details are in my notes. Main conclusion is that we will drop using the dendrometers in the fall and I should reach out to the people at OpensLab to see if they can help me troubleshoot the dendrometers. We also talked about which classes I should and shouldn't take in the fall. We talked about the nutrients and I told her that I was concerned trees were showing nutrient stress symptoms. So she gave me green light to give them liquid nutrients. I searched lots of papers to figure out what would be a good nutrient concentration to add to the trees because we want to mimic natural conditions. I asked Dan's opinion and he brought fertilizer from the greenhouse. In his opinion, this will work perfectly and will provide fast release nutrients to the plants. 
Mao and I met at 3pm, so I can show her how to take the shoot elongation measurements and finish the pheno monitoring. We had to leave before we finished because we had a lab meeting. We presented the trips we had been doing in the following weeks. I came back to Totem after to finish phenomonitoring and take the measurements on the paper rulers. 

\def\day{\textit{June 7, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Started at 10am. I kept on looking at how much fertilizer I should add to the trees. It's very ambigous, so I decided to add very small amounts at first and readjust later on. For now, I diluted the solution Dan gave me by half with tap water. I added ~125mL of liquid fertilizer to all plants today. In the afternoon, I downloaded all the data from the hobo loggers that were already in the greenhouse. Then, I added 22 temp/light hobo sensors all over the greenhouse, because I strongly suspect that we will have a big light effect because of the forest behind the greenhouse. The plants at the front of the greenhouse most likely receive much more light than the ones at the back of the greenhouse. I also took some time to move my bird feeders because I caught a squirrel eating in them. 
\begin{itemize}
	\item Figure out fertilization and do it -- done
	\item Reserve camping
	\item deliver Mao's package -- done
	\item
\end{itemize}

\def\day{\textit{June 7, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at noon, mainly to take care of the plants at Totem. I finished setting up the light meters. I decided to remove logging in the temperature data,  because anyway it's extremely biased because the sun directly hits them and make them really hot. I need to finish the greenhouse design with them in. 

\def\day{\textit{June 10, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
\begin{itemize}
	\item check new hobo sensors -- done
	\item update the greenhouse arrangement with all the new loggers
	\item make sure irrigation is back on -- done
	\item start writing up the methodology on hobo loggers and fertilizer -- done
	\item shoot elongation protocole -- done
	\item DEFENETILY do the apical shoot death monitoring -- done
	\item Write to Mao to tell her what she will need to do -- done
	\item phenomonitoring -- done
	\item load shoot elongation measurements in excel file -- done
	\item write to Lizzie and colleagues to tell them that I won't be checking my email -- done
	\item Move Alru back to the soil pit -- done
	\item Weed all the plans -- done
	\item update the pheno monitoring and shoot elongation of all the segi that I removed from the experiment. 
	\item Email Lizzie about her class-- done
	\item return book to Amazon
	\item Add notes to the labgit on chambers
	\item email Melina regarding the greenhouse -- done
	\item Inventory of trees outside at Totem -- done
	\item Clean up the mess at Totem -- done
	\item Answer Lizzie's email on Google Drive issue. -- done
	\item start loggers at the top of Greenhouse -- done
	\item add csv file description for aserdiversity -- done
	\item text dan to spray again -- done
\end{itemize}
I worked a lot on the methodology today. I wrote up on the hobo loggers, fertilization, shoot elongation monitoring. I also added a file of apical shoot monitoring because many trees have a dead apical shoot. Therefore, I don't think we will be able to estimate their inital biomass. 
\par I followed up on the git issue regarding fertilization
\par Asevdiversity: reuploaded the methodology text and added column description to the .tex file as requested by Lizzie. 
\par Big day! I did pretty much all the things I listed today! I finished with weeding all the plants in and out the greenhouse. I replied to Lizzie and Mao to finish. Break is tomorrow!

\def\day{\textit{June 11, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 12, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 13, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 14, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 17, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 18, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 19, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 20, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 21, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 24, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 25, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 26, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 27, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{June 28, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}