\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{May 1st, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Last few miles of my trip with Charlotte. For our last morning, we went to Billy Frank NWR. 41 species. Heard a Sora. 
We headed to Vancouver and set my things up in the afternoon. 

\def\day{\textit{May 2, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf{Christophe+Deirdre + Ken + Selena}
\par 
\textbf {Task}:Orientation
Move Cool/Cool treatments back to Totem for following species:
- Acne
- Bepa
- Prvi
\par 
\textbf {Reasons}: These species don’t look too happy in the chambers and most of the replicates are fully leafed out
\par 
\textbf {Results}: Deirdre got me orientated on the project and trained me on the phenological monitoring.
I met with Ken and Selena so we can move the first batch of species Cool/Cool treatments back to Totem:
Acne
Bepa
Prvi
Alru
*** we decided to move also Alru as they are probably dead. 
Plants in chambers watered 
\par 
\textbf {Comments}: I need to request Totem truck a few days before I need it – Dan was using it that day. Therefore, we used the Subaru to move the trees. 
POT Effect : The roots for Bepa and Alru seem to be limited by the pots. Need to repot them ASAP. 

\def\day{\textit{May 3, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe+ Ken}
\par 
\textbf {Task}:Water B3 – not currently irrigated.
Set up irrigation lines in B3
Print shoot elongation rulers
Map how many drippers per line
Make these decisions:
1. Whether or not to abandon dendrometers
2. Abandon Alru and Segi
3. Which potting mix to use
4. Pot size to use
\par 
\textbf {Reasons}: Don’t want plants to dry
Since we will install more lines and the irrigation system is at max capacity, we need to make sure to not overload it to avoid not having enough pressure. 
On decisions:
1. Many problems (too much time required to trouble-shoot them)
2. Not doing great either at Totem or in the chambers
3. Should I add clay (raise water retention) to the mix. Should I use the leftovers from last year?
4. 4-gal: extremely time consuming to build, repot and heavy to move around. 2-gal: should be enough for current growing season. 
\par 
\textbf {Results}:Installed irrigation in B3. On one line, there is a fitting missing (will need to ask Dan to figure it out). In the mean time, I watered them manually.
Ken counted drippers on each line and noted them in my note pad. 
Decisions:
*** had a quick chat with Fredi in the afternoon to ask for his opinion.
1. Agreed to abandon dendrometers for now. We will reinstall them later in the summer.
2. Agreed to abandon Alru and Segi
3. Agreed to reuse potting mix from last year
4. 2-gal. 
\par 
\textbf {Comments}:Need to fix the water hose: leaking from 2 places. 
Reasons to abandon Alru and Segi: 1. Loss of many replicates. 2. Even if they would suddenly come alive, there wouldn’t be a meaningful difference between the plants in the chambers and the ones outside.  
Since we reuse potting mix from last year, it’s probably low on nutrient content. We need to solve this – should create a Git issue on this. 

\def\day{\textit{May 4, 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\par 
\textbf {Task}: Repot Acne and Bepa
\par 
\textbf {Reasons}: 2 most advanced species and the most limited by pot size
\par 
\textbf {Results}: Repotted Acne and Bepa
\par 
\textbf {Comments}:Time to repot Acne: 2 hours for +- 30 trees. 
Time to repot Bepa: 3.5 hours for +- 60 trees, which includes removing dendrometers.

\def\day{\textit{May 6, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe + Ken + Deirdre}
\par 
\textbf {Task}: Find a solution for paper rulers.
Go to Staple (Amazon package never arrived)
\par 
\textbf {Reasons}: Talked with Deirdre and Ken about how we should avoid what happen last year where the rain ruined the rulers. Taping the end of the ruler should avoid them falling. Also helps the tape sticking to the ruler. 
\par 
\textbf {Results}: Decided to use packaging tape to protect the end of rulers.
Went to Staples. Going to return everything I bought.
\par 
\textbf {Comments}:Notes on repotting: I fill a layer at bottom and compact it very tight (about 1-2 inches depending on how much soil there is in the old pot. I delicately remove the tree from its current pot and place it in its new home. I had pot mix to fill the gaps. I compact the sides with my fingers and add mix until the pot is full. 

\def\day{\textit{May 7, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\par 
\textbf {Task}: Tape the end of the rulers.
Paint Acne to mark from which point the shoot will be measured. 
Install rulers on Acne
\par 
\textbf {Reasons}: Installing rulers on trees is really time consuming. I thought I will try only 30 replicates (Acne B1) for now. I will keep going once all the species have had at least one shoot elongation measurement. 
\par  
\textbf {Results}: 99 rulers have their end taped. 
Acne B1 have their rulers.
Acne B1-B2-B3 were all measured.
Set up a calendar
\par 
\textbf {Comments}: It takes 0,73 minutes to tape the end of 1 ruler.
It takes 2.5 minutes to install the ruler on 1 tree. *** I am not too good at this right now so I will probably get faster soon. 

\def\day{\textit{May 8, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe+ Ken}
\par 
\textbf {Task}: Paint on Bepa and Prvi
Shoot elongation measurements on Bepa and Prvi
\par 
\textbf {Results}:Repotted Prvi
Painted Bepa+Prvi
Measured Prvi+Bepa
\par 
\textbf {Comments}: I need to buy more medical tape.
2 trees completely dead for prvi.
Need to figure out what to do with resprouting and when there is more than 2 trunks. 


\def\day{\textit{May 9, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Christophe
\paragraph{}
\begin{itemize}
    \item Answered a few emails.
    \item Move back Segi that I removed previously to the greenhouse (warm spring treatements).
    \item Phenological monitoring for all species
    \item Paint Pist/Poba
    \item Measure shoot elongation Pist/Poba
    \item Water plants in CC
\end{itemize}

\paragraph{Comments} Once I realized Segi were turning back from brown to green, I decided to bring them back to the experiment. Issue 12 on Git describes this.

\textbf{On methods for shoot elongation}: I always measure the center shoot of Pist. If there is no “central” shoot, I put a red dot on the measured shoot. 

\def\day{\textit{May 10, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\paragraph{}
Painted Segi, Quma and Acma.
\paragraph{}
\begin{itemize}
    \item Took pictures of all Segi replicates as I want to keep track of their color change.
    \item Ken removed some dendrometers.
    \item Shoot elongation measurements for Segi, Quma and Acma (both in field and CC)
    \item Plants were rotated and watered in the chambers
    \item Worked 2 hours on irrigation and greenhouse arrangement.
    \item Started pruning Alru and weeding plants.
\end{itemize}
\paragraph{Comments} I was not feeling well this morning, so I came in at 11 and finished at 8:30. I realized pruning Alru, weeding the plants outside the greenhouse will take many hours. Dan and I will install automatic watering for trees outside the greenhouse.

\def\day{\textit{May 13, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\begin{itemize}
    \item Moved Poba/Pist back to Totem
    \item Repoted Pist (all of them)
    \item Brought home and aped the end of roughly 100 rulers in the evening
\end{itemize}
\paragraph{Comments}: Pist show root limitation. Will post pictures on git. Poba didn’t need to be repotted as they were already in 2-gal pots from the cuttings planted in March

\def\day{\textit{May 14, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\paragraph{}
Personal appointment to fix my car. So did mostly computer work. Emails, git issues, update data, etc. Came in for 3 hours in the afternoon to move around some plants and start weeding some from outside of the greenhouse.

\def\day{\textit{May 15, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe+Ken+Justin}
\begin{itemize}
    \item I bought tape.
    \item Taped the end of rulers.
    \item Shoot elongation measurements of:-Acne -Bepa -Poba -Prvi
\end{itemize}
\paragraph{Comments}:
Before May 15, Hobo loggers were very much exposed to the sun. Therefore, they are heating which I assume influences the temperature sensor greatly. 

\textbf{On phenological monitoring of Pist}: Justin and I talked about it and we figure that for this species, from 1-2-3 are the shoot elongation and 4 is leaf emergence. This species elongates its shoots before the needles emerge. Justin will start an issue on this with upcoming pictures. 

\def\day{\textit{May 16, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf{Christophe+Justin}
I came in at 9:30 and Justin at 10
\begin{itemize}
    \item We did shoot elongation measurements for : -Quma  -Segi
    \item We took pictures of Segi, Quma and Pist for phenostages. Justin started an issue to figure out Segi phenostages.
    \item We watered and rotated Acma, Segi and Quma (in chambers).
    \item 
    \item I installed white paper with a half pot to protect Hobo loggers from getting sun heat.
    \item I installed a bird feeder.
\end{itemize}
\paragraph{Comments}
: left early for an appointment at ICBC.
\def\day{\textit{May 17, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe+Selena} 
I arrived at Totem at 11am. I had to go back to ICBC to get my Driver's license done. Selena arrived at Totem at 11am. 
\begin{itemize}
    \item We installed the paper rulers on Poba and Quma, both in the greenhouse and in the chambers.
    \item I had to buy more medical tape.
    \item I fixed a couple of leaks on the irrigation system .
    \item I saved the vegetable plants for Dan that he forgot in the truck.
    \item I weeded almost all the plants outside of the greenhouse. I finished at 8:30.
\end{itemize}
\def\day{\textit{May 20, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\begin{itemize}
    \item 
    \item Started a git issue on nutrient addition and answered a few emails.
    \item I removed 2 species from the chambers: -Quma -Acma
    \item I took the hobo loggers from those chambers as I want to install them at Totem. CC4 and CC1 are the ones removed.
    \item I placed all the Segi in the Walk-in chambers.
    \item Since the Subaru was very dirty from all the plants moved around, I cleaned it with a very bad vaccum that I found in the basement.
    \item First visitor at my bird feeder! Black-capped chickadee. I am very excited.
    \item I did the phenomonitoring for all trees.
    \item Put back drippers in Quma
\end{itemize}

\def\day{\textit{May 21, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
\begin{itemize}
    \item Took some time to learn Latex.
    \item I attended a talk on AI in Academia with Deirdre. Then we talked about a few questions I had regarding how to organize my data, the summer plans of the lab and other stuff.
    \item Then I chatted with Mao about our respective projects and how Mount Rainier is going to be like.
    \item Then I answered a few get issues and emails.
    \item 
    \item I changed the photoperiod in CCWalkin and set the remaining chambers to a constant 10 PAR and 15 degrees so they consume less energy.
\end{itemize}

\def\day{\textit{May 22, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe + Ken}
I started marking the rulers and Ken arrived at 10. 
We finished marking the rulers at 12 and Ken went to get extra paper rulers because we forgot some trees on Friday. 
I talked with Dan, we will shrink the irrigation system, remove the compost and cut the grass around the greenhouse. 
I talked with Deirdre regarding the car battery 
A crow stole my granola bar :(
We finished taking the measurements around 3. I left as I had another apppointment at ICBC to register my car. 
I went to Costco during the night to buy a new car battery for the lab.
\paragraph{Comments}:

\def\day{\textit{May 23, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Started the day with some readings on growing season extensions. 
Added two quick notes in my obsidian slip box. I have been procrastinating on this and should be more consistent.
I answered emails to Lizzie, Deirdre and Mao regarding egret retreat, lab meeting, rbs retreat, etc.
Submitted my expenses to Lizzie
Lizzie agreed to the switch of car responsibility from Deirdre to me. 

\def\day{\textit{May 24, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe }
Went back to ICBC to register my car in BC.
Came back at Totem to clean the greenhouse so it's presentable for my presentation on Sunday
Last step of fixing the irrigation has been done with Dan in the morning. We 
I changed the Subaru's battery with the one I bought at Costco. I charged it so it's at maximum capacity with the car charger at Totem.
Met with Deirdre and Mao at 1pm to discuss:
-Egret retreat, -Mao's fieldwork, -General plan for the summer
I also mentioned to them that I thought of removing the Segi from the chambers because they've been there for a long time and because of the power outage that will happen the day after (Saturday). We agreed to remove them and place them back at Totem.
I moved the Segi back to Totem, and placed the irrigation back into the pots.

\def\day{\textit{May 25, 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Came in at 5pm to prepare my presentation for tomorrow. 
I installed dendrometers on trees and prepared a bunch of graphs.
I finished cleaning the greenhouse

\def\day{\textit{May 26, 2024}}
\def\weekday{\textit{Sunday }}
\subsection*{\weekday, \day}
\textbf{Christophe + Justin}
Came in at 8am to set up my monitor and my presentation.
Justin came in at 10:30 to take pictures of my presentation while I was presenting the graphs to him! 
Grad students from Isabelle Laforest's lab came to my talk
Another student from Ontario also came. 

In the night, I went to the reception. It was very nice. Mao and Deirdre were also there, and I saw Steven K who just arrived in Vancouver. 
\def\day{\textit{May 27, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
CSEE conference
Deirdre and I met with Patrick from biochambers in the morning. We decided to meet with him on Friday morning and since Deirdre won't be able to attend, Mao will join. 
Attended many talks
In the night, I went to the grad/post doc mix at Koerners. 
\def\day{\textit{May 28, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe} 
I started the day with a visit of the greenhouse for the students of Steven K lab. Then I came back to the nest with them.
Attended many talks once again

\def\day{\textit{May 29, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe + Britany}
Came in at 9:30 and Britany at 11.
Started marking the rulers for shoot elongation measurements. We finished the measurements with the metal ruler at 2pm. I went back to the nest to attend the last talks. Britany finished logging in the paper rulers marks. She didn't finish it. I fill finish logging in the data tomorrow. Had a chat with Dan regarding the mildew that's attacking the Acne. We decided to spray them with systemic fongicide. It was done the same day by Dan

\def\day{\textit{May 30, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
First work day after the conference. Lots of things to do:
\begin{itemize}
    \item Bring 20 plants in the lab to start testing the dendrometers
    \item Attend Deirdre and Britany's graduation and take pictures of them -- done
    \item Meet with Rob Guy -- done
    \item Update nutrient issue to inform Lizzie/Freddi -- done 
    \item Check Segi W/W 14 and 15. They were switched, so I wanted to make sure that phenomonitoring was done properly -- done
    \item Phenomonitoring
    \item Add archive folder to fuelinex repo  -- done
    \item Email Lizzie for next week meeting -- done
    \item Student profile on Forestry site -- done 
    \item Review notes from last year's egret retreat -- done
    \item Start issue on disease management -- done
    \item Answer Lizzie on asevdiversity -- done
    \item Finish setting up Hobo loggers 
\end{itemize}

\def\day{\textit{May 31, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe+Mao+Britany}
Started the day with the interview with Patrick from Biochambers. It went great! He answered many concerns I had with the chambers and found possible reasons why the trees were not doing great in the spring. 
After that, I started repotting the Segi around noon. Britany arrived shortly later. She left at 1:30 and I finished alone around 4pm. I worked on my computer for the rest of the day, 

\def\day{\textit{June 3, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
Started the day by answering many emails. I answered the git issue on nutrient depletion which took my quite some time. I also finished installing the dendrometer. I did this just so I can check if they are all working.
Met with Mao at 3:30pm to discuss worklearn. We updated the offer and will send to Lizzie to confirm the info with her. 





