\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{1 August 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Last day of fieldwork with Andy. We finished AV06 and headed to another site that is a 40 minute walk away from the parking lot. We did 1/4 of it and left. On our way back, we saw a wasp nest that has been eaten recently by a bear. It's funny because Andy was just telling us about this. 

\def\day{\textit{2 August 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
We woke up, packed and said farewells to Andy and then headed to Paradise for our hike. We saw a bear cub near the parking lot! We were short on time, so we did it fast and had to cut halfway. We left for Seattle at 11:30. Before Justin took the train, we had bubble tea. He left around 6pm. Mao, Britany and I had amazing Korean food in Tacoma and stayed in a Mariott there. 

\def\day{\textit{3 August 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
We woke up at the hotel and went to get some breakfast. Mao hated her drink which tasted like red bull. It was guava and passion fruid. I loved it! Then we went to get some car seats and gear for the field.\\
We picked up Avery in the afternoon and went to get ice cream. I had butter pecan and salted caramel. \\
We headed to Longmire. 

\def\day{\textit{4 August 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
First day of Mao's fieldwork!. We woke up at Longmire campground and left for Nesquali House. We dropped our stuff there and headed to AV06. \\
Mao showed us how to install dendrometers and how to core trees. One problem we encountered was flatening the bark. I proposed getting a file. We then left early so we could go in town to buy a bunch of stuff. I cleaned the house when we got back because it was disgusting. 

\def\day{\textit{5 August 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Second day of fieldwork. I work with Brittany. We managed to finish half of AV06

\def\day{\textit{6 August 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
NA
\def\day{\textit{7 August 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
NA
\def\day{\textit{8 August 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
I forgot my boots this morning and got stung twice by stepping on a wasp nest that was eaten by a bear. We finished the plot and left around 6. We hiked back up towards the falls. 

\def\day{\textit{9 August 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Started the day with a meeting that Mao requested. Change of plan: I will be working alone for coring trees and Britany will be installing all the dendrometers. We drove to Longmire camground wifi spot. After hiking up to the trail and started the plot. We managed to finish 12 out of 16 plots.\\
We drove back to Nisqually House, got changed and drove to the nearest town to eat at a Mexican restaurant, called Puerto Vallarta. We also did the groceries. Mao and I had a talk in the night. 

\def\day{\textit{10 August 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
We finished the stand near Longmire campground. Britany and I still had a bunch of dendrometers left to install when we finished coring the trees, so we helped Mao and Avery.\\ We finished around 1pm, hiked down, had lunch and left for the Devil's Club plot. It beautiful but it sucks. Trees are enormous and it's mossy everywhere. However, the Devil's club sucks the life out of me (slight exageration). \\
The cores are hard to extract because the trees are so big, plus the Devil's club are usually in the way. I fell from a log, but didn't hurt my self that much. \\
We finished half of the plot and went home. We took half of the day off. Avery, Britany and Mao went to the beach. I didn't feel good so I stayed at the house and slept for most of the afternoon. 
 
\def\day{\textit{11 August 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
Slow morning today. We left to go back at the Devil's club stand. It was terrible again. The THPL are probably the hardest trees I have cored so far. They are so big, it's hard to extract the cores.\\
Mao got stung 8x today.  We finished around 2pm. I saw 3 whisky jacks. 

\def\day{\textit{12 August 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Britany felt under the weather today, so she stayed home. We went to Sunrise Stand and parked at the Reflexion lake parking lot. We hiked for 15 minutes before realizing that we weren't at the right place. \\
Fortunately, the other plot wasn't far. It was full of yellow cedars which was very nice. Very steep thought.

\def\day{\textit{13 August 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Rainy and cold today. We realized it wouldn't be safe to work in these conditions. We drove back home. 

\def\day{\textit{14 August 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
We left again around 8:30 for AE10 and Paradise. It's cloudy and cold again for the second day in a row. We hiked all the way to paradise when we realized that it was very wet and slippery. We decided it wasn't safe to work so we hiked down and went back home. Avery, Britany and Mao went to core 6 new trees from the first plot we did because they weren't great when we first cored them. I took a nap and worked on my project. Mostly for the fall biochambers schedule and looked at the data Justin and Ken recorded.
Lizzie and Jonathan came to meet me at the house. We discussed gps points and how the fieldwork was going. I made fritata for dinner.

\def\day{\textit{15 August 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
We left at 8:15. Cloudy and cold again. We went to meet Lizzie and Jonathan at Longmire campground at 8:30 and headed up to AE10. We forgot the box with all the data sheets which slowed us down a bit. We finished the plot around 10:30 and headed to Paradise. We hiked up and started the plot. On our way up, we tried to trouble shoot working in these plots when it's raining.

\def\day{\textit{16 August 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Going back to Vancouver! We left at 8:00, first stopped at UW to drop off the tree cores and dendrometers. Then we went to REI to buy hiking poles and bear box. We went to eat at the very cool Korean Restaurant Mao, Britany and I went when we stayed in Tacoma. \\
After, I picked up my back-pack that I found on marketplace. No wait at the border. I dropped the car off around 10pm. 

\def\day{\textit{19 August 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
I went for an apartment visit this morning. I arrived there and the landlord told me he would increase the rent by 500\$. I declined it. I was really upset. Then I went back to UBC to pick up Avery, Britany and Mao. We left around 11am. \\
A lot of wait at the border (something like 2 hours). We at Chipotle on the road and arrived at UW around 4pm. We picked up the new vest, increment borers and left for MORA. \\ 
On our way, we stopped at Costco, Safeway and Home Depot. 
We arrived at the campsite at 9pm. We set up the tent and went to bed

\def\day{\textit{20 August 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
First day of the second trip! Pretty cloudy and cold\\
We left for Paradise around 8:30. We hiked up and managed to do more than half of the plot in during the day. The spikes and poles work really well.\\
We forgot the foot of the tent at Longmire, so we had to drive back there. We arrived at the campground around 6, made dinner and went to bed quite early.

\def\day{\textit{21 August 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Cold and cloudy again. We left at 8:20, but we had to buy a stove for the backpacking trip we will be doing on Thursday. We bought a Coleman. We went back to the campground because Avery forgot his rainjacket and it started to rain. We drove to Paradise\\
I found another way yesterday to get to the stand faster. It's 12 minutes longer to drive to the pulloff, but it's like 100 meters away from the stand. So we saved a lot of time. However, Mao didn't like it because we damaged the plants.\\
Mao got stung twice by wasps.\\
We finished at 1:30pm, walked back to the car and drove up to Paradise for the hike. Since I had a lot of work to do and because I was tired, I didn't do the hike with them. \\
I went to gift shop. I bought a patch for Charlotte. It's not very nice. I also found an expensive JET boil. I bought it for the backpacking trip. I went to another gift shop. I found another patch that is nicer, but stupid expensive. I bought it and returned the other one. \\
The team came back. Mao got her first alergic reaction and she isn't feeling great. I was concerned and we discussed all night what we should do about that. I also contacted Lizzie so she knows what's up. I am happy about the sticker I found. 

\def\day{\textit{22 August 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Cloudy and cold this morning. Mao and Avery are going to town for an appointment with a doctor so we can get an epipen prespription. In the meantime, they dropped us off at TA01. It's so nice. Really easy to walk around and locate the trees. We managed to finish coring my trees around 1:30pm. While Britany and I were discussing what we should do next, we heard Avery scream. They came back from town with 2 epipens! \\
I helped them finishing their trees and we drove back to the campsite at 4:45pm. We went to the gift shop when we went to get wifi. I found a very beautiful limited edition patch for the 125th aniversary of Mount Rainier. I bought it and bought the same, but sticker version to stick it on the lab bear canister. \\
Mao and I made Chili for dinner. After, it started raining and Avery and I walked so we could go take a bath in the hot springs. No bath going on there. It's a swampy hot spring, so we took a quick dip in the very cold river. \\
It's raining a lot now as I write these lines. We went to bed at 9:12pm. 

\def\day{\textit{23 August 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Very wet. We got up and ate breakfast standing because the picnic table is soaked. We left for site AB08 that was a 30-minute drive and 10 minute hike. I found an elk leg that was relatively fresh. We kept on going and found the site. I had the hemlocks that day. The first quarter of the stand sucked. In one plot I had to core 6 trees before finding one that wasn't rotten. It was probably a zone affected by root rot. \\
I only had time to finish one quarter before lunch. While eating, I prepped my straws better so I could be more efficient in the afternoon. \\
The second half of the day was better tree-wise. Only for the quality of the trees because it started raining a lot. It was hard to keep the straws dry. At some point during the day, Mao asked if we wanted to keep going. I really wanted to get that site done, because we knew that it would rain tomorrow. So we kept going. \\
We finished aroung 5:30. Mao cut her finger after corring their last cedar. \\
Since it was still pooring rain, we decided to go eat out in packwood. We went to the local brewery first. I got some very nice nachos. A full size that I ate for myself. It was delicious. \\
Then Mao really wanted fries, so we went to the saloon. We got fries and Mao got me a beer. We sat a table with a very nice couple from Texas. We got some interesting discussions about health care, school, how weird Texas is and why the lady was not vaccinated but the gentleman was. 

\def\day{\textit{24 August 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
Very wet again. We left for AO03 quite late because we took some time to pref the old straws because their are more waterproof. The drive wasn't very long, probably around 20 minutes. However, the hike was about 40 minutes. Very beautiful and easy though. The stand was gorgeous; magnificient huge douglas firs and red cedars. We started the site and I got a tree core stuck in my borer on my second tree. I couldn't get it out until the end of the day. In the afternoon, I got stung by a wasp near the spot where we left our backpack.\\
I finished my trees around 3pm and helped Mao and Avery to finish their trees and then Britany. Then I hurt my knew. We packed and hiked back towards the car. \\
On our way back, I got stung again by a wasp and then 5 minutes later, I got stung in 3 different places even though I never saw the wasp itself. It really hurt!. \\
We drove back to the campground, had leftover chili for dinner and went to the wifi spot. I replied to a bunch of emails and we went to bed. As I am writting these lines, Mao fell just fell on my mattress while getting in the tent. It also just started leaking, so that kinda sucks.

\def\day{\textit{25 August 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{26 August 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{27 August 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{28 August 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{29 August 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{30 August 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{31 August 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
