\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{1 November 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Came in at 9. Worked on my lit review until 12. I had to meet Adam to discuss bugs about Tina. Kept working on lit review until we interviewed Randiv. It went fine. Then I met with Deirdre to figure out my bib tex. Kept working on my lit review until 5. Then I worked on the dendrometers and started cookies. Left at 7:30.

\def\day{\textit{2 November 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
Did math most of the afternon
\def\day{\textit{3 November 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
Got my bib file working.

\def\day{\textit{4 November 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Came in at 9am. Read papers and finished the highly cited subset I made for myself in September! Now I will move on to Lizzie's greatest hits. \\
I scanned 3 cookies today. Tina is going great! It scanned 4 big cookies over the weekend, and the stiching now takes a fraction of the time as it did before. \\ 
I worked on my math homework for a good part of the afternoon\\
Finished reviewing my NSERC proposal and sent it to Lizzie\\
Met with Natasha regarding Lisa's project.\\
Met with Ailene for coring trees at the Arboretum\\
Interviewed Yijia\\
Finished going through treespotters tree IDs and sent it to Lizzie\\
Started a few cookies and left at 6:30pm.
\def\day{\textit{5 November 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{6 November 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Felt depressed this morning as Trump won. I went to monitor senescence and budset for the trees that are now all at totem. It took me a little more than 2 hours. Met for egret. Came back to the office, worked on the math assigment and attended Sally's office hours at 1. Worked on the math assigment all afternoon. Left at 4:30.

\def\day{\textit{7 November 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Biomath this morning. Came back to the office, filled in gaps I missed in the class and then worked on the tree cookies with adam to fix some bugs tina has. I cleaned the lab with Mao.

\def\day{\textit{8 November 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Lit review this morning. Set up 7 cookies. Left for eco evo

\def\day{\textit{9 November 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
EcoEvo
\def\day{\textit{10 November 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
EcoEvo and set up 6 cookies

\def\day{\textit{11 November 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
took the day off, I was too tired.

\def\day{\textit{12 November 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Came in at 9 for lit review until 2pm. Worked on CGS-M until 5:40 and went to see Anora. 

\def\day{\textit{13 November 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Came in a 9 for pheno monitoring of trees at totem. Few individuals left to measure. Came back and worked on math assigment until 2pm. Mis tasks in the afternoon including treespotters proposal and final edits on summary CGSM.

\def\day{\textit{14 November 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Biomath. Came back to the office worked on my FRST303 questions and watched last week's lecture. Attended the class and after reviewed Sally's quiz questions. In the afternoon I worked almost exclusively on the tree cookies and analyzed their rings. I had bugs. The samsung SSD got corupted which slowed down my progress a lot. I had to transfer 400go of files onto the SanDisk SSD which took 3 hours. Started 7 cookies in the evening, one of them didn't work. I switched the dendrometers and started a new batch which took 1 hour and a half. 

\def\day{\textit{15 November 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Came in at 9. Watered Lisa's plants and started 1 big cookie. I prepared for my meeting with Neil Pederson. We met for 40 minutes. It was great! We will meet again next Friday to discuss the progress. Then I read and took notes on 4 papers. \\
Emailed Sally O for project ideas for Biomath301. \\
Worked on summary for CGS-M, transcrip, and others. It should be good to go\\
Emailed Lizzie for recap of the week\\
Worked on dendrometer troubleshooting. I am so sick of this.\\
Started 10 cookies for the weekend.\\
Left at 8pm

\def\day{\textit{16 November 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{17 November 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
Worked on cookies

\def\day{\textit{18 November 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Came in at 9. Read 4 papers in the morning. Finish proposal for the arboretum permit and sent to Lizzie. Did biomath quiz. Worked on egret in the afternoon for 2 hours. Scanned the last cookies. Left at 4pm for Jon's plants. Replied to  a bunch of emails in the evening.

\def\day{\textit{19 November 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Biomath class this morning. Worked on timeline, finished it. Office hour and frst 303 after. TA meeting. Updated timeline descriptive. Went for biomath lab. Came back and worked on questions frst 303. Finish with dendrometer troubleshooting and left at 7pm. 

\def\day{\textit{20 November 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Came in at 9. Finished budset monitoring! I measured senescence for Poba i.e. the only species remaining that still has leaves. Came back to the office, attended egret meeting. Worked on the math assigment, met with Sally to discuss the project. Worked on forestry exam questions and on dendrometers. Left at 7pm.

\def\day{\textit{21 November 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Biomath class this morning. Came back for forestry class. Worked on exam questions and then on tree cookies for the whole afternoon. Adam and I realized there were important issues with the stitching process which is going to slow me down a lot. I prepared the meeting with Neil and then worked on dendrometers. Left at 8pm

\def\day{\textit{22 November 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Came in at 9. Met with Neil at 9:30 for 45 minutes. He was really helpful again. Then I read 3 papers. I added my last expense to the drive. I emailed Lizzie so we could meet to talk about DPI. I won't be able to work on the cookies until that issue is resolved. It is the core of the analysis and if I can't get it right, there is no point of going further. Met with teaching team in the afternoon to work on tree ID questions. I finished miscelleanous tasks and went to Brevaginos. Came back to the lab, finished troubleshooting the dendrometers and cleaned my bench. Watered Lisa's trees. Left at 8pm. 

\def\day{\textit{24 November 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
Worked on tree ID quiz for 3 hours. 

\def\day{\textit{25 November 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Read 4 papers in the morning. Then I spent most afternoon working on the tree ID exam tomorrow. Left at 6:30

\def\day{\textit{26 November 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Came in at 10. Office hour, then worked on tree ID exam. Attended biomath lab and worked on my model with Asad in the afternoon. Came back to the office and finished edits for treespotters proposal.

\def\day{\textit{27 November 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Came in at 9. Worked on CGSM all morning verifying that everything is fine. Then I had lunch with teaching team. Went to monitor the trees at Totem. Came back to the office and worked on the math assignment all afternoon.
\def\day{\textit{28 November 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{29 November 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{30 November 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
