\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{July 1, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
This morning, I tried adding a table of contents to this dailylog. I don't know why it's so complicated, but I could't figure out a way to do it. I let that go. 
\par Then I tried installing Stan on R, as Deirdre suggested. It didn't work either. I will ask her when she's back from vacation. 
\par I worked for most of the afternoon on my script for the shoot elongation measurements. It doesn't look too bad! I needed a break, so I went to install hobo light loggers in the climate chambers so I can see how much light they are giving to the trees when they are in there. I also brought back the bepas that were in the lab to totem field. 
\par at totem, I monitored bud set for prvi and took pictures of the acne. For prvi, I think they are far more advanced than I was expecting. Some of them seem to already be at complete dormancy. For acne, it's confusing. Mildew have impacted them a lot. They show very tiny leaves, but they have been there for a while now, so as Fredi told me, it might just be the upcoming scales that will cover the bud. 
\par I removed the drippers from the Segi. I will put them back on Friday. After discussing with Fredi, we thought giving them a water break would be good.
\par I came back to the office to finish what I started. 
\par I modified slightly Fredi's notes on budset so they keep going after 4 (5,6,7,0)

\def\day{\textit{July 2, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Lizzie, Mao and I talked about getting a power bank for the lab. Lizzie ordered it. It should arrive on Friday.
Fredi and I discussed about literature reviews, how he does them and where I should start\\
Britany and I discussed the fertilization plan and we figured that there are no good amount we could add to the trees. We rather run in the problem of the studies used seedlings and not saplings. A lot of them were using \% of N, P or K of leaf tissue and not actually of much mg were added to the plants. I also discussed this with Fredi. He suggested looking at the atmospheric deposition, but I argued that this is for a whole ecosystem and figuring out how much nutrients a sapling is actually getting would be hard and perhaps impossible. So I just decided to be consistent and add nutrients again this week. I'll do this just after we weed all the plants.  

\def\day{\textit{July 3, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe + Britany}
We started the shoot elongation measurements. As I won't be there next week, I showed Britany how to take the measurements. We didn't have time to log in the paper ruler measuremnts.
\par Dan delivered the organic spray bottles to keep killing the powdery mildew (some of the new shoots are getting it again). He also delivered the fertilizer. It's the same one as last time. I will fertilize the trees perhaps on Thursday
\par I asked him to reduce the watering of all trees to once a day, in the morning for 15 minutes, instead of 3x a day.
\par In the afternoon, I started a new cv file on latex\\
Deirdre and I talked about litterature reviews\\ 
I finished my power point presentation for the lab meeting tomorrow on research tools.\\
Deirdre and I tried to trouble shoot the installation of Stan on my computer. It still doesn't work. I'll try again maybe tomorrow -- although I won't have time with the budset and other things 

\def\day{\textit{July 4, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe+Britany+Ken+Selena+Justin}
Came in at 8 to check the egret coordinates. I checked the data, and then cleaned the entries I could. Then I went to Totem to meet Britany and figure out budset. She worked on this during the week, and we needed to figure out some other species. Acne is most likely ongoing budset, so we took photos of those. We did the same for the oaks and the pines. These two were tricky, because some of the oaks are doing a second flush, but some don't seem like they will. For the pines, I had no photos to base budset on, so we discussed what stages they could be. I'll talk to Fredi about that tomorrow. \\
At 1pm, Ken and Selena arrived to weed the plants. Justin arrived at 2:15pm and we finished at around 3. Britany and I finished taking photos of some good budset examples after I went to pick

\def\day{\textit{July 5, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Britany and I finished loggin in the data for shoot elongation and budset. Then I finished the document for budset, I still need to figure out pist.\\
I met with Lizzie in the afternoon to talk about litterature reviews, who will take care of my experiment while I am gone. She asked me to ask Britany to meet with rob with ken and Justin.

\def\day{\textit{July 6, 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
 I came in to finish egret coordinates cleaning. I managed to fix almost all issues. Some remain.\\
 I did the map for egret also\\
 I went to totem to fertilize the trees for the second fertilization of the season. I used the same method as the first time. I diluted the fertilizer by half and added 125mL.

\def\day{\textit{July 8, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret Retreat!
We started the day with some break-out teams. I was with Fredi to try to figure out question 2. We came back 1 hour later and debriefed. In the afternoon, Lizzie showed me how I could proceed with the experiment design with a for loop. 

\def\day{\textit{July 9, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret Retreat!
I arrived late this morning. We worked for 2 hours before leaving for the ferry. On the ferry Lizzie helped me with some tasks I had.

\def\day{\textit{July 10, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret Retreat!
We went to the pub for beers, onion rings and fried pickles. We went to the eastern point to see if we could spot whales but we couldn't find any...

\def\day{\textit{July 11, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret Retreat!
We finished around 4pm after a long discussion about authorship. I found this talk very insightful and got to address my concerns of me being a co-author. We worked for a little bit after and drove dan to the plane in the evening.

\def\day{\textit{July 12, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret Retreat!
Last day of the retreat! Not the most productive on a coding basis, but we had a lot of fun! We did the 4hour hike Lizzie recommended. It was beautiful. The weather was great. 
We came back to the cabin, packed, cleaned the place and left. Lizzie bought us an early dinner at the pub right next to the ferry. The second ferry after we left Saturna was left so we had a chance to have Deirdre give us a small talk about phylogeny\\
In the ferry I worked on my code to clean coordinates. I thought I solved the issue, but I didn't. I came back home around 10pm.

\def\day{\textit{July 15, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
I had a quick chat with Ken about the monitoring of shoot elongation and phenology in the following weeks. We walked to the lab after to start packing the gear for Smithers. We left at 12pm after saying bye to Lizzie.\\
The drive went pretty well. We saw a wild fire on our way up. We stayed at the camping Juniper Beach. Worst ever!! It was so warm (about 32o)

\def\day{\textit{July 16, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
\def\day{\textit{July 17, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
\def\day{\textit{July 18, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
\def\day{\textit{July 19, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
\def\day{\textit{July 20, 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
Went birding at Round Lake in the evening, since we came back early and it was the first day we were not exhausted.

\def\day{\textit{July 21, 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Smithers
We hiked up, but on our way, we did soil moisture since it's been 48 hours for the last rain. 
We finished dendrometer measurements and seedling monitoring for plot 11 and 14. They had so much. We lost the toothpicks and anyway we wouldn't have enough. We replaced them with popsicle sticks instead.
We saw an American Three Toed Woodpecker at plot 11!!!
Since we finished early, we hiked up to the summit. Mao and Deirdre stayed just after plot 17. It was so beautiful!
We went for beers at the local pub. Really smokey.
\def\day{\textit{July 22, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
We did a small hike to Hudson Bay Mountain because I saw on eBird that a rock ptarmigan has been spotted. We finally saw one,  but I still can't identify it...
\def\day{\textit{July 23, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 24, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 25, 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 26, 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}



\def\day{\textit{July 29, 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 30, 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 31, 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
