\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{1 October 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Biomath class in the morning. Came back to the office, replied to a bunch of emails and helped Mao empty the lab car.\\
I had my office hours followed by FRST303. Really interesting! It was on leaf colouring. We then had our teaching meeting and discussed the midterm.\\
Worked on my math assignment and then went to BIO301 lab. I went to Assad's office hours after this.\\
Left at 5pm to clean the car and fill it up.

\def\day{\textit{2 October 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
IMPORTANT: CHANGE OF CHLOROPHYLL METER TODAY TO SPAD 502 since the one we had died. 
Came in at 9. Worked on my math assignment. It's a mess and I don't get anything. I went ot pick up the SPAD from Rieserberg's lab. Then, I went to monitor the trees at Totem. It tooke me about 2 hours. \\
I attended Sally's office hours to for help with the assigment.\\
Went to monitor senescence with Mark in the climate chambers. Watered the plants and rotated all of them.\\
Finished the day with budset monitoring in the greenhouse. 

\def\day{\textit{3 October 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Bio math class. Sally gave me the opportunity to redo the assigment now that I knew how to do it. So I did it before attending my FRST303 class. Very cool today! We talked about budset and dormancy. Sally A asked if I could give a quick presentation of what I do with my trees and leaf senescence. It was nice. Some students seemed interested! \\
I left earlier to have lunch with Britany, Mao and Justin.\\
I came back to the office, worked on some stuff and left for the tree walk with Sally. It was so fun. It was cool to finally see some students. I walked back to forestry and finished the day with questions for frst 303. It took me roughly 3 hours.

\def\day{\textit{4 October 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Rainy and cold today. I arrived at 9:30. I worked on some miscellaneous stuff until 10 when I met with Adam and Mao to discuss the tree ring imaging device. After this, I worked on my litterature review. I don't know why but I felt really tired today. \\
I backed up hobo devices in the greenhouse and installed one in the climate chambers to check light intensity. 

\def\day{\textit{7 October 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Started the day with organizing my week. I finished some miscelleneous tasks left over from the previous week. I also read a little about SPAD. \\
Did math from 10 to 1pm. \\
Prepared meeting with Lizzie\\
Had meeting with Lizzie
Worked on lit review. Only had time to read 1 paper. I left at 6pm.

\def\day{\textit{8 October 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Math class this morning. Followed by my office hours, class then TA meeting.\\ 
Worked on math, then went to the lab. Came back to the office and work on math assigment.

\def\day{\textit{9 October 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{10 October 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{11 October 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{12 October 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{13 October 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{14 October 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{15 October 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{16 October 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{17 October 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{18 October 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{19 October 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{20 October 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{21 October 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{22 October 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{23 October 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{24 October 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{25 October 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{26 October 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{27 October 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{28 October 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{29 October 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{30 October 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{31 October 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
