\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{1 September 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
I went to the campus in the morning to fix the biochambers. It took me a couple of hours. I had to fix the drains, clean the filters. It was a mess. 

\def\day{\textit{2 September 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Had something to do downtown this morning. Then, I got an apartment visit and arrived on campus around 10:30 to meet with Fredi so we could discuss about the senescence monitoring and other stuff. \\
Then Mao and I met with Mark for an interview at 1pm. \\
I worked on the chambers again in the afternoon.\\
I worked on a figure Fredi and I discussed it could be good to have to visualize the warm fall treatment. I updated my futur daily logs and finished the one from August. \\
I emailed Patrick for the schedule of the fall treatment. 

\def\day{\textit{3 September 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
I arrived at the office around 9am. Since it's Imagine day, I didn't have the biomathematics class. I emailed a bunch of people and went to check how the bio-chambers repairs were going. It should be done by the end of the day. However, two of the lights won't be installed for my experiment. 
I met with Lizzie in the afternoon to talk about senescence monitoring, the frequency at which I should monitor this, etc. \\
I kept on doing some figures for my treatment schedule in the climate chambers.

\def\day{\textit{4 September 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Arrived at the office around 9:00 to interview Anoya.
At 10:00 I went to fix the walk in chamber only to realize that there is no drain to evacuate the water. That will require me to remove the plants every two days from the chambers.
Then I went to Totem to take pictures of the plants to monitor senescence. It took me 34 minutes to photograph 180 trees. I might not even ever use this data.\\

I met Teresa at 11:30 to talk about the agroforestry class.  We talked for a bit and then walked to the class. I attended the class and I think it will be very cool and interesting! \\
After this, I went back to Totem to finish taking pictures of the plants and Mao joined me so we could start monitoring senescence. It took about 45 minutes/species and we had 5 species to monitor. We discussed what Fredi told me to do i.e. estimation of green leaf coverage and chlorophyll content. We both guessed the percentage by comparing to what 100 \% green leaf coverage would look like. Then we measured the chlorophyll content by selecting 3 leaves randomly and taking one measurement. \\
We did 3 species and then start moving the plants to the climate chambers. We came back to the greenhouse, measured the 2 remaining species and Mao left as it was 7pm already. \\
I kept moving the plants, until it was too dark and my fingers were so tired, I could barely hold the pots. I stopped at 9pm.

\def\day{\textit{5 September 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
I started the day with Sally's class at 8am. I talked to her after the class so I could register to it. Then I went to Totem to finish moving my plants.\\
I started by performing the nutrient boost treatment. I added nutrients to all the CSCF_nitro that remained there. Then I added nutrients to the WSWF_nitro for pines that I didn't have time to move yesterday night. For I added 250mL of the solution that wasn't diluted (as opposed to what I added to the plants during summer. This means I added 4x of what they had during the summer. \\
Then I took an inventory of how many replicates were left from my segi. For this, I took some replicates from the nutrient boost treatment and will be further moved to the non-nutrient boost treatments further during the analysis. For now, I think it is better for them to retain their original name so I don't confuse things. The notes I took on this can be found in the following directory: /fuelinex/notes/miscellaneous/segireplication.md \\
I moved the pines and the Segi to the walk-in climate chamber and added nutrients to all the WSWF_nitro replicates that were already in there. 
So far the room arrangement are: CC1 : Acne. CC2: Prvi, CC3: Bepa, CC4: Poba, CC5 : Quma and the walk in : Pist and Segi.
I came back to the office, uploaded the photos from the greenhouse, responded to some emails and then headed to my agroforestry class for the first tutorial of the semester.

\def\day{\textit{6 September 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
Small day today!
I went to check in on my plants and watered them. 
I started reading for biomath and agroforestry. I updated some notes for my experiment and read Patrick's email on the schedule for biochambers. He recommended I add far red light, but I decided that for consistency, I will only ramp the light and temperature better than for the spring treatment. \\
I replied to a bunch of emails and wrote to Mark so we can start working next week.\\
I received the fan for the greenhouse. 

\def\day{\textit{9 September 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
Came in around 9:30 and started with a list of things I will need to get done this week.\\
I read chapter 1 for biomath and chapter 1, 2 and 3 for agroforestry. I finished assigment 1 for BIO301.\\
Just so I can help Mark with git, I redid the sandbox exercice. \\
I finished reading Piao and al 2016. \\
I emailed Mark to appoint him with the different tasks needed to be done. 

\def\day{\textit{10 September 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
Biomath class this morning. Even if I did all of my readings, I didn't understand anything. I went to the post office after to mail the extra gps I bought.\\
Then I attended the session for new grad students. 90\% was boring and not useful.\\
I got some pizza, went to eat it at my desk, worked on my schedules and then attended the lab for BIO301. It was terrible. My team doesn't care and is completely lost. I went to Assad's office hours and he helped me a lot for the assigment.\\ 
I came back to the office, finished assigment 1 

\def\day{\textit{11 September 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
Mao and I started monitoring senescence at 8am. Mao left at 9:45am to attend her class. I kept going until 10:45 and then left for BRC to attend our bi-weekly egret meeting.\\
We discussed our issues. I updated everyone on the provenance issue and we figured there are two steps in this issue that we aren't sure what to do about. We finished around 11:30. I left for the office, quickly had lunch and left for pharmacy building to attend my agroforestry class.\\
I filled out my expenses. \\
I came back to the office, did my biomath readings and Mark came to join me at 2:15. We left for the greenhouse to finish senescence monitoring. I took about 40 minutes and we left for the climate chambers. He stayed until 5 and I finished by myself. We rotated the plants in their chambers, watered them and monitored senescence.\\
Schedule changed for the one of Sept 11.
I left Forestry at 7pm. 

\def\day{\textit{12 September 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
Biomath class this morning. Then Mao and I came back to the office. I scraped out the papers I will  read for my literature review. I finished around 11am and started reading 2 papers that were not really relevant for my project, so I got through them quickly. \\
I installed Hobo connect on the lab computer. 
 
\def\day{\textit{13 September 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{14 September 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{15 September 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{16 September 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{17 September 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{18 September 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{19 September 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{20 September 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{21 September 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{22 September 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{23 September 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}

\def\day{\textit{24 September 2024}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}

\def\day{\textit{25 September 2024}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}

\def\day{\textit{26 September 2024}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}

\def\day{\textit{27 September 2024}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}

\def\day{\textit{28 September 2024}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}

\def\day{\textit{29 September 2024}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}

\def\day{\textit{30 September 2024}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}