\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{January 6th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
First day back after Holidays!
Worked all morning on tree cookies ring measurements. I am almost done with all the ALNINC.  I have trouble identifying some of them.
I attended the first class of FRST 304. 

\def\day{\textit{January 7th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked most morning on litterature review. Worked on a couple of tree cookies. Read the first slides of ECC class. 

\def\day{\textit{January 8th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on tree cookies in the morning and on lit review in the afternoon. 

\def\day{\textit{January 9th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked all day organizing my lit review notes. About 100 done. 

\def\day{\textit{January 10th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked all day organizing my lit review notes. Read 4 papers

\def\day{\textit{January 13th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Flew back to Vancouver from Montreal. Worked one egret in the airplane for 1 hour. Then I worked on notes and read 2 papers. 

\def\day{\textit{January 14th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
First day back in the office!  Came in at 9:30 and read the paper for Tuesday's class. Then went to class. Came back to the office, finished some stuff on egret and went to Bayesian class. Left at 6pm.

\def\day{\textit{January 15th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret meeting, followed by scrum, cookies and seminar. Went for sushis, then bayes class and came back to the office to work on lit review. Left with victor around 5:30 to go to Dolph's place for pizza and beers!

\def\day{\textit{January 16th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Finished reviewing antarctica's paper. Went to class. Came back to the office and worked mostly on egret's homework and litterature review. Left at 6 and went to muay thai.

\def\day{\textit{January 17th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30, read 4 papers in the morning and worked on lab meetings and miscellaneous tasks in the afternoon. Left at 7.

\def\day{\textit{January 19th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on cookie measuring for 3 hours.

\def\day{\textit{January 20th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked all morning and beginning of afternoon on bayes homework and then met with Lizzie. Came back to the office, worked on lit review and helped wenhuan on pull requests. Left at 5:30.

\def\day{\textit{January 21st 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30 to start tree measuring. Left at 10:30. Went to CONS310 class, then worked on Lizzie's new figure and went to bayes class. Left right after.

\def\day{\textit{January 22nd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked and very much advanced lizzie's new figure! Went for cookies with victor and mao. Mao brought me a birthday cinnamon role cake! Went to seminar, sushis and bayes class. Left right after.

\def\day{\textit{January 23rd 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on todays paper for cons310.
\def\day{\textit{January 24th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Met with Neil in the morning and on lit review in the afternoon. TA meeting in the afternoon. Went to bevraginos and trivia. 

\def\day{\textit{January 27th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked all day on bayesian homework.

\def\day{\textit{January 28th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Measured height block 2 with Colette from 8:30 to 10:30, went to class, came back and got the coffee prepared for bayes class. Went there and left after. 

\def\day{\textit{January 29th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Victo phd presentation in the morning, then egret, then cookies, then seminar, then bayes class. Left after it. 

\def\day{\textit{January 30th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Measured height block 2 with Colette from 8:30 to 10:30. Went to class, then came back to the office, worked on McKenzie king application and met with Lizzie in the afternoon. Worked on tree cookies until 6pm.

\def\day{\textit{January 31st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on lit review until noon. Then worked all afternoon on tree cookies. I finished the first round of measurements, but a lot of them need to be resanded and rescaned. Finished the day with emails. 
