\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{December 1st 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Finished measuring diameter and height with Tess! Realized that the ovens at totem never reached the desired temperature. closed the vats and see how it goes. removed segi from the ovens. Met with victor and mao for provenance pop up. in the evening, i removed the dirt and washed out the B1 and B3 for segi. Took the xterra home to fill gas. Left at 5:30

\def\day{\textit{December 2nd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Moved the segi in the ovens. Updated issues and worked on plotting model outputs. TA meeting. Bayes modelling group. Came back to the office, worked on thesis until 6.

\def\day{\textit{December 3rd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked a bit on egret, and then on gdd model mean plot. Pop up, then worked on model all afternoon and some on my thesis. Updated the figure of what I'm testing. Left at 6.

\def\day{\textit{December 4th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30. Statistical rethinking, then checked the crossdating of my cores again and changed some stuff. Worked on cleaning my data set so I'm ready to start a model. Went to Jeremy fox seminar and went back to the office and worked on my thesis all afternoon. Worked on thesis until 5 and then on crossdating and some plotting empirical data for coring treespotters. Left at 7.

\def\day{\textit{December 5th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
Came in at 9. Statistical rethinking, then worked a bit on checking topic sentences on my proposal. Met with Tess at 10:30. Weighted 1 bloc of segi. I went to totem, grabbed the bepas that I removed from the ovens, and for the ones that were too long, I cut and because they stayed for 4 days at 45C, I brought them back to forestry and put them in the ovens after I the 2 blocs of segi. Tess removed most of the needles of the remaining pines. I weighted the last two blocs of segi alone and cleaned the lab a little. 

\def\day{\textit{December 6th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at noon. Removed soil and washed roots of all poba. Left at 3.

\def\day{\textit{December 7th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{December 8th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Remove 2 blocs of bepas in the oven, then brought pobas back to forestry and placed one bloc in the oven, and the 3rd bloc of bepa in the other oven. Worked on thesis most of the morning and met with lizzie in the afternoon. Finished working on thesis. Almost done. TA dinner in the evening.

\def\day{\textit{December 9th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Updated an issue in the morning, then drove to Washinton for Nexus interview. Graded exams in the evening. 

\def\day{\textit{December 10th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Updated thesis and reviewed Mike's probability theory chapters. We attended his class in a room. Worked on posterior sums for gdd leafout model. Left at 6.

\def\day{\textit{December 11th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking, then worked on slope figure for wildchrokie growth model. Removed poba and bepa from ovens. Cut pobas and taped them for tomorrow. Ran errands in the afternoon and had appointment after. Finished grading essay in the evening. 

\def\day{\textit{December 12th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Came in at 9:30. Finished cutting B3 and taping them and placed them in oven. Went to totem and cleaned my dirt washing clothes. Came back and cut pobas and placed B2 in the oven at 12pm. Went to the office and worked on wildchrokie growth model figure. Worked with Nolan at 1pm on weighting the trees.

\def\day{\textit{December 13th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked a bit on wildchrokie model

\def\day{\textit{December 14th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
TA exam in the morning. Worked for 2 hours on wildchrokie model

\def\day{\textit{December 15th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe and Nolan}
Came in at 8. Cleared the whole greenhouse: removed ceiling fan, camera, extension coord, lamp, tools. I piled the pots and other stuff. Came back to the lab, removed B2 from ovens, then checked the Acsa with very long ring. Then went back to the lab and met Nolan, we weighted B2, then removed B3 from oven and weighted it. 

\def\day{\textit{December 16th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 17th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 18th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 19th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 20th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 21st 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 22nd 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 23rd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}

\def\day{\textit{December 24th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf{Christophe}
