\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{March 3rd 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked from home mostly on commitee meeting presentation. Monitored budburst in the afternoon with Charlotte.

\def\day{\textit{March 4th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Personal appointements in the morning, then Lizzie's class and worked all afternoon on commitee meeting presentation. Praticed it in the night with Charlotte.

\def\day{\textit{March 5th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 and practiced commitee meeting presentation and overviewed papers for the lab meeting. Went to cookies and seminar and practiced for my committee meeting. Got a lot of very helpful feedback. 
Came back to the office, answered emails and worked on part one for the project. Left at 6 with Charlotte.

\def\day{\textit{March 6th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Monitored budburst and started to install hobo loggers again. Didn't have time to finish though. Took pictures for budburst. Came in only for Lizzie's class. While Charlotte and I were walking in Stanley Park, I received positive news from NSERC! 

\def\day{\textit{March 10th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Studied for tomorrow's test. In the afternoon I went to Totem to monitor phenology. I stayed there for 3 hours to replace trees at their place and clean the greenhouse. First day of Acne budburst! Left at 6:30.

\def\day{\textit{March 11th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 10 and entered the data from my voice recording. I started going through the comments I got from my commitee meeting. Then went to the test. Came back and met with Mao to discuss egret and worklearn. Worked on egret worldflora package all afternoon. Left at 6.

\def\day{\textit{March 12th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on egret before the meeting, then attended Mike Whitlock's seminar and came back to the office. Worked on project all afternoon with my teamates.

\def\day{\textit{March 13th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 and measured phenology at Totem. Started wattering the trees to remain moisture similar to the trees outside. Came back to forestry and attended class. Tried to work on tree cookie guidelines but it didn't work. Then I finished taking notes on the feedback I got during my committee meeting practice and started updating my presentation. \\
Then I went back to totem, and repotted the last block of Pist and all the sequoias. I finished wattering all the trees and installed the covers on the hobo loggers. I am still missing a couple. Took me roughly 4 hours. Left at 6pm. 

\def\day{\textit{March 14th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked from home this morning mostly on my committee meeting presentation and emails. Came to the office and worked on WDC and met with one of my mentee. 
\def\day{\textit{March 15th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 16th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 17th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 to chat with Milos about Wall's award. Came back to the lab and chatted with adam so he could fix the guideline tool for the cookies. Then, I added the guidelines and left to Totem to monitor phenology. I also took a bunch of photos! Took about 2 hours. \\
Came back to the office and prepped for my meeting with Lizzie. Met with her and worked for 2 hours on my outline for the wall's award and a little on my commitee meeting presentation. Worked for an hour on cookies. Left at 6pm. Met with the team at 7pm before submitted part 2. 
\def\day{\textit{March 18th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 19th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 20th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 21st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 22nd 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 23rd 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 24th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 25th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 26th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 27th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 28th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 29th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{March 30th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf
