\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{July 1st 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 2nd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Drove from Maine to Boston to pick up the cores. Nikita opened the doors for me and we left for Montreal with them at 5pm. Crossed the border around midnight.

\def\day{\textit{July 3rd 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Mounted the cores all day. Took 8 hours.

\def\day{\textit{July 4th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Removed the tape from the cores. Sanded a first round, but the sand paper I had was not compatible so I could only do one round of rough grid sand paper.
\def\day{\textit{July 5th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{July 7th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked a bit on model in the morning 

\def\day{\textit{July 8th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
CSEE

\def\day{\textit{July 9th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
CSEE

\def\day{\textit{July 10th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on my model all morning and replied to git issues. 

\def\day{\textit{July 11th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on my model and egret issue. Flew to YVR in the night. Devina and Nolan took the weeds from all all the pots today.

\def\day{\textit{July 12th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Arrived at Totem at 9. Realized the trees haven't been watered in weeks. So I contacted Lizzie to confirm what I should do. I took VWC of all trees, then monitored budset because I suspect this drought has triggered early budset. I restarted the irrigation manually for 1 hour to give them a good amount. I was supposed to give all trees nutrients but because of all of that, we decided to postpone till we're back from Smithers.

I don't know yet who shut down the water, but most importantly when.

\def\day{\textit{July 13th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
We were supposed to leave for Smithers today, but Mao is felling really bad, so Nolan and I will leave in the afternoon instead. 
We left at 2, made it past hope to arrive at a car crash site where we waited for 1 hour before turning back because the estimated wait time was 4-8 hours... We had to do a very long detour and stayed in Meritt instead. We arrived at 9 to realize that there was a music festival that would go till 6 am! Terrible. We barely slept
While Nolan was driving I input all the recordings I made from the day before for VWC and budset
\def\day{\textit{July 14th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Left Merrit after a rough night and made it to Smithers around 10pm. We made a couple of spots, one of them was to see pelicans which we did! We had to stop at Prince George because Mao didn't pack the quadrat and only 1 ruler. We also made groceries.

\def\day{\textit{July 15th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
First day of fieldwork! Quick chat in the morning to discuss the plan and double checking we had all the gear. It went super fast. We finished 10 sites (1 to 10)

\def\day{\textit{July 16th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Second and last day. We finished everything and hiked all the way to the top at the end of the day.

\def\day{\textit{July 17th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Went past Hazelton to do a beautiful and hard hike.

\def\day{\textit{July 18th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Last day in smithers, we hiked back door of opal ridge and didn't see ptarmigans. Left early afternoon and slept past Quesnel at a nice campground with goat and donkey. However there's a train track right next to it so don't recommend even though it's really cheap

\def\day{\textit{July 19th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Left in the morning and arrived in Van at 4pm. Worked on my expenses in the car. Went back to UBC to grab my laptop I forgot in it, put the shop vac in the car and put the solar pannel in the car too.

\def\day{\textit{July 20th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked a bit on my expenses and unpacked. 

\def\day{\textit{July 21st 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30, received the news that I got the silver medal. Worked on model update for wildchrokie and read a bunch on what should be the next step. Then worked 2 hours on Statistical rethinking course. Tried to advance on fuelinex model, but with no success. Then updated my outline. Met with Lizzie to discuss experiment and PhD. Went to Totem and looked for tools to dig a hole. Left at 6:30

\def\day{\textit{July 22nd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in late as I had appointments in the morning. Worked on stat rethinking course. Read a bunch	about what should I do next for wildchrokie model. Emailed Etienne L. Finished preparing presentation and cleaning photos for lab meeting tomorrow. Started preparing NSERC. 

\def\day{\textit{July 23rd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Came in at 9. Trained Nolan on budset monitoring. Worked on egret clean treatments. Did some scanning tests with the cores for the arboretum with Devina. Lab meeting.

\def\day{\textit{July 24th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Finished wrapping up my stuff before the retreat, including. Met with Rob. Added the last nutrient addition to all the trees. Met with people at UdeM for NSERC.

\def\day{\textit{July 25th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 26th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 27th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 28th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 29th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 30th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret retreat!
\def\day{\textit{July 31st 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came back to the office, met with Rolando for ovens. Monitored chl for comparisons between the 2 tools. Brought the car back in the morning after filling the gas. 