\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{October 15th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
First day back in the office! Monitored senescence with Tess. Came back to the office, worked on midterm exam and went to BRC seminar. Updated model wildchrokie issue and other stuff. Replied to emails. Worked 3 hours on midterm exam. Left at 5

\def\day{\textit{October 16th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked from home this morning. Mostly worked on lit review and proposal. Worked a bit on my model, but been struggling with stan because the model won't run properly.

\def\day{\textit{October 17th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30. Statistical rethinking then worked on proposal. Met Tess at totem to make a third round of measurements for chlorophyll tool comparisons. A lot of leaves fell, so low sample size. Worked for 2 hours on proposal, then on model wildchrokie. Updated pop up provenance for egret. Updated issue for parameterization wildchrokie. Emailed people.

\def\day{\textit{October 20th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
On Satuday and Sunday, I tagged all 500 paper bags for fuelinex biomass collection. 
Didn't feel well today. Worked a bit on statisical rethinking, replied to git issues

\def\day{\textit{October 21st 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking. Worked on different itterations of my model to fix tree depth exceeding. Worked on section 1.3. for proposal and finished grading for TA. Left at 6pm.

\def\day{\textit{October 22nd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
brc seminar. Worked on 2 sections of my proposal. updaed model. ran a heavy model overnight (took 9 hours)

\def\day{\textit{October 23rd 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
excellent progress on proposal. tried accessing midge. failed. updates on model

\def\day{\textit{October 24th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
came in at 9. statistical rethinking and wildchrokie model for the rest of the day. I chatted priors with Ken. Tried to access midge. Success. Left at 6pm. 

\def\day{\textit{October 27th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
Came in at 9. Senescence monitoring with Tess. Acne and Quma are now done and majority of Prvi are too. We finished senescence in 45 minutes, then we measured diameter for all acne and quma and height for acne only. This took 1h30. Then I started washing off the roots off some acne. It goes pretty well. Came back to the office, updated stan code, tried to launch it on Midge, but failed because the version is too old.

Went back to Totem and removed dirt from all trees in B2 and finished washing off B1.

\def\day{\textit{October 28th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Replied to git issues from home this morning. Met Tess at Totem to measure height for all quma. There is one late individual that hasn't lost all its leaves, but they aren't green. It likely won't grow anymore, so the measurement were performed on it anyways. 

We removed almost all paper tapes, except the ones from B3 because it was raining a lot. 

Then I started washing off roots from bloc 2, but I didn't have time to finish. I came back to the office, got the Xterra, packed B1 and brought it back to the lab. TA meeting, then put B1 in the oven at 70C at 2pm. Then bayesian group and came back to the office. Worked until 5:30 on plotting wildchrokie empirical data.

\def\day{\textit{October 29th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Brc seminar, worked on model and proposal

\def\day{\textit{October 30th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Brc seminar, worked on model and proposal. Washed all B2 and B3. Took 2-3 hours.

\def\day{\textit{October 31st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Moved B2 and B3 in the ovens and weighted B1 for acne. Took a bit more than 1 hour. 
