\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{May 1st 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on cores and cookies until 3pm. Monitored phenology and shoot elongation. Recorded myself for the trees without paper rulers. Except Quma. First day I noticed mildew on the acne. 

\def\day{\textit{May 2nd 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Marked the Qumas for shoot elongation and measured them. Bought way to many plants. In the afternoon, I worked on cookies, emails and other stuff. Went to bevraginos and sprayed the acnes of the potassium bicarbonate. 

\def\day{\textit{May 5th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on cookies for one hour, then worked on cleaning species names for egret until 4pm. Monitored trees. Left at 6.

\def\day{\textit{May 6th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked from home this morning, mostly on egret. Came to the office, worked on cleaning cookies and finalizing data scraping. At 4, I went to help mao cutting her mounts, then we cleared a raised bed off the weeds that would be cool to grow some corn and sunflowers. Left at 7pm.

\def\day{\textit{May 7th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Worked on egret, attended meeting. After, I worked on my wildchrokie data simualtion until 2pm. Then finalized wildchrokie core verif and left at 2:45 for a medical appointment. 

\def\day{\textit{May 8th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30 because I had errands to run this morning. Came back to the office and worked on cookies until 1pm. Then I wrote a bunch of emails and then went to Totem. Installed paper rulers on Quma, monitored phenology for pist and Quma, then monitored shoot elongation on paper only since I am alone today. Skipped prvi because it doesn't elongate much anymore and will start monitoring them every second week. 

\def\day{\textit{May 9th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Worked on lit review, then on model. Went to totem to add nutrients to the non nitro boost treatments. Same amount as the nitro dose in april. Left at 7 pm.

\def\day{\textit{May 12th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30 and worked on cookie cleaning and crossdating all day. Monitored phenology. Weeded a raised bed and planted some carrots. Left at 6pm. 

\def\day{\textit{May 13th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Devina}
Started at 8am and worked on cookie cleaning. Then worked on model. Met with Devina at 3pm to read the shoot elongation measurements from the past 2 weeks. Weeded the trees from bloc 1. Left at 6 pm. 

\def\day{\textit{May 14th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Appointment at the garage. Worked on egret while waiting. Went to buy compost for the garden plants I bought. Brought back the Xterra at the lab and stored the fertilizer. Worked on egret all afternoon. Scanneed some cookies I forgot.

\def\day{\textit{May 15th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Devina}
Came in at 9 for shoot elongation with Devina. We finished around 11:30am. Then I monitored phenology. Came to the office, worked on my model for 1-2 hours and updated my git issue. Then worked on egret until 5:30pm.

\def\day{\textit{May 16th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on sourcing all codes in wildchrokie. Then read gelman and hill and kept going on statistical rethinking class on youtube. Reviewed asevdiversity manuscript. Emailed and did my data summary of fuelinex. 

\def\day{\textit{May 19th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
No one in the office today! Worked on lit review, almost all day. Except when I worked a bit on treespotters cleaning code and sanded left over cores. Phenomonitoring 

\def\day{\textit{May 20th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Sent cookies so they can get guidelines to Mao. Then personal appointment and worked all afternoon on my outline. Marked sequoias to prepare them for shoot elongation measurements. Left at 6pm.

\def\day{\textit{May 21st 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in and attended egret meeting, then worked on cookie cleaning and scraping the last few. Met with Neil to discuss cookie scraping and worked on that all afternoon.

\def\day{\textit{May 22nd 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Personal appointment, then met and trained Nolan for shoot elongation. We weren't done, but I met with Rob to discuss nutrient addition at 2pm. Came back and finished shoot elongation measurements. Left at 5.

\def\day{\textit{May 23rd 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Finished shoot elongation measurements this morning with Nolan, at 10:30. Weeded the last bloc -- bloc 3. Came back to the office and worked on many git issues. 
\def\day{\textit{May 24th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 25th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 26th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 27th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 28th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 29th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 30th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{May 31st 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
