\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{April 1st 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
After 4 hours of refreshing on NSERC's website, I finally got my response for CGS-M AND I GOT IT! Super happy. Then went to seminar which was interesting and got to speak to the speaker at lunch. Came back to the office, finished my cookies and kept on mounting my cores. Had an appointment so left at 3pm.

\def\day{\textit{April 2nd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30 and worked on cookies on microscope till 11:30 and went back to the office. 

\def\day{\textit{April 3rd 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Lizzie's class in the morning. Monitored the trees and watered them for the ones inside of the greenhouse. Interviewed Nolan in the afternoon and worked on sanding the cores.

\def\day{\textit{April 4th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Sanded the cores. Scanned the 4 left over cookies. Worked on cleaning script for the cookies and went to wine and cheese in the evening and came back to the lab to scan the first round of cores.

\def\day{\textit{April 7th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 and scanned the second round of cores. Worked on expenses and prepared meeting with Lizzie. Met with Lizzie, scanned 2 rounds of cores. Worked a bit on egret. Monitored phenology, came back to the lab and scanned the last cookie. Left at 6:30

\def\day{\textit{April 8th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Last class! Presentations. Went well. Worked on cookies in the afternoon, some code for that project and prepared treespotters. 

\def\day{\textit{April 9th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on egret until 10. Interviewed Oscar and attended egret meeting. Met with Jonathan to talk about McGill. Came back to the office and worked on paper rulers. I couldnt print them.... Gave up and worked on cross dating the cookies with cores to figure out if we had growth for 2023 or 2022. Left at 6pm. In the evening I taped all the paper rulers. 

\def\day{\textit{April 10th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on crossdating the cores. Phenomonitoring after. Came back to the office, met with Norm to help me set up the printer. Worked on crossdating the cores and finished the easy ones. Printed paper rulers 
\def\day{\textit{April 11th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Mark}
Came in at 8:30 with Mark. We started marking all the trees for shoot elongaton. We measured Prvi manually as they are the most advanced. I added fertilizer on all the trees, \textbf{except} Nitro boost treatments. I added 125mL of non-diluted fertilizer mix from the greenhouse, which is twice what we gave the trees last year.\\
Came back to the office, met with Sally A. and gave her a visit to the greenhouse. Went back, finished irrigating Segis and went to beers.

\def\day{\textit{April 13th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in the afternoon to build a table. Worked on it for roughly 3 hours. 

\def\day{\textit{April 14th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Ken}
Came in at 9. Printed cookie images for Boston and preped for the trip. At 1:30pm, I went to Totem, finished my table and monitored phenology with Ken who will be taking care of the trees while I am in Boston next week. Then I took a bunch of photos of budburst. I added irrigation lines and moved stuff around. Started putting the drippers in. I finished marking the Bepas for shoot elongation. Left at 6pm. 

\def\day{\textit{April 15th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Appointments in the morning. Came to the office at 11. Printed a bunch of stuff for Boston and started reading on models for wildchrokie. Then I sharpened the increment borers and met with Victor to talk models. Preped the rulers and implemented the notes I took during my meeting with victor into a latex document. Went to totem to mark Pobas. Left at 5:30.

\def\day{\textit{April 16th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Mark}
Came in at 8:30 to install paper rulers at Totem with Mark.	We finished installing them on Bepas and Pobas. Since quma haven't started to elongate we are still waiting for these. I also put back the drippers into the pots, but the water still isn't on. Came back to the office and worked mostly on planning stuff for Boston. Met with Lizzie in the afternoon. Went back to Totem to work on the irrigation. Started Gaant chart for 2025 objectives. 
\def\day{\textit{April 17th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 18th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Going to Boston

\def\day{\textit{April 19th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Boston! Dailylog in coringtreespotters repo

\def\day{\textit{April 20th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Boston! Dailylog in coringtreespotters repo
\def\day{\textit{April 21st 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Boston! Dailylog in coringtreespotters repo
\def\day{\textit{April 22nd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Boston! Dailylog in coringtreespotters repo
\def\day{\textit{April 23rd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on lit review this morning. Had frozen yogurt with Mao and started working (very slowly) on wildchrokie model. Stopped working at 5pm.

\def\day{\textit{April 24th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 25th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 26th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 27th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 28th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 29th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{April 30th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
