\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{February 1st 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Kept working on cleaning measurements for fuelinex

\def\day{\textit{February 3rd 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on lit review. Left at 6
Sanded cookies for 3-4 hours.
\def\day{\textit{February 4th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
No class today! Worked on lit review and started outline thesis.
Sanded cookies for 3-4 hours and looked at them on the microscope.

\def\day{\textit{February 5th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 and worked all day on egret clean coordinates that is still not cleaned well. Left at 8pm.

\def\day{\textit{February 6th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Tree measurements at totem. Got to finish two blocks for diameter, but didn't start the third because the trees are covered in snow. Alex from Michaletz's lab came to get some sequoias. Then attended class. Came back in the lab, installed dendrometers and set up a bunch of cookies to get them scanned. Left at 6.

\def\day{\textit{February 7th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 8th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 9th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 10th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 11th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 12th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 13th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 14th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 15th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 16th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{February 17th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Small day! Worked on plane tickets and airbnb for the trip in Boston. Did email and other stuff.

\def\day{\textit{February 18th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9 and worked on lit review. Then I kept going on my outline and started my committee meeting power point. Then I went to Totem and painted the trees that were missing paint. Left at 7pm. Scanned cookies

\def\day{\textit{February 19th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 10am. Worked on figure for treespotters data and emailed lizzie to tell her I realized I missed 4 trees in the dataset. Worked on hobo temp data for a little  bit and on my power point. I worked all afternoon on my phenological monitoring script to make some nice figures for my commitee meeting! Left at 7pm. Graded exams all night.

\def\day{\textit{February 20th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30 after grading exams in the morning. Worked on lit review this morning and then on hobo temp script. Sanded some cookies and scanned 4 of them. Worked again on hobo temp script to add to my experimental design figure! Then scanned cookies and left at 6. 

\def\day{\textit{February 21st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on commitee meeting presentation and on some figures. Prepared the repotting party

\def\day{\textit{February 22nd 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Repotting party! From 10am to 6 pm, many people and I repotted almost all the trees. The first bloc for all species was repotted in 3-gal pots using new soil mix, excluding segi. Blocs 2 and 3 were repotted using left over mix from phaenoflex. 

\def\day{\textit{February 23rd 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Graded exams
\def\day{\textit{February 24th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Graded exams, emailed a bunch of stuff. Worked on egret species for 3 hours

\def\day{\textit{February 25th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9am. Worked on figures for my committee meeting. Maped tree spotters tree. Left at 6:30. Came back home and worked on treespotters until 9:30 pm. 

\def\day{\textit{February 26th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30 to move back the pots where they belonged, I started remarking bloc 3 with paint as some of it was starting to fall. Went back of the office for egret meeting, went for cookies and worked on it. Measured the last diameter measurements for bloc 3 and some sparse trees. Realized that some prunus started to budburst! So started monitoring them today. Checked other species and they are still dormant. 

\def\day{\textit{February 27th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Prepared for Lizzie's class and started reading the paper discussion paper. Then attended the class, came back to the office, worked on committee meeting presentation and met with Lizzie. Went back to Totem after.

\def\day{\textit{February 28th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked from home this morning. Then worked on committee meeting presentation all afternoon and went to Totem to monitor budburst. 
