\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{November 3rd 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on eco evo presentation all morning. In the afternoon, I washed off the dirt of all Quma B1. I removed Acne B2 and B3 from the ovens, weighted and bagged them. Took roughly 2h30. Left at 6 pm

\def\day{\textit{November 4th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on eco evo presentation, since it was sunny outside, I went out and removed dirt from QUMA B1 and B2, but didn't have time to wash the roots. Came back with B3 and placed the trees in the oven at 12:30. TA meeting. Eco evo presentation work and attended bayes working group. Eco evo presentation work until 6:30pm

\def\day{\textit{November 5th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Practice for eco evo presentation, then studied SR and went to BRC seminars. 

\def\day{\textit{November 6th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Appointment at the garage in the morning. Came back to Totem. Washed out Quma B1 and B2. Took 2 hours. Implemented comments from the presentation in PP. Worked on proposal and am almost done.

\def\day{\textit{November 7th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Tess and I went to Totem, measured all prvi and only height for pist B3 and B1. B2 height and all diameter are still required for Pist. We went back to forestry, and weighted Quma and bagged them. Worked egret pop up all afternoon and some other issues. I went back to totem at 4pm and worked until 7:30pm. in the dark, removing dirt from all prvi. 

\def\day{\textit{November 8th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Tagged missing paper bags.

\def\day{\textit{November 10th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9am. Went to totem washed dirt off prvi and brought them back to forestry. Placed half of them (not by blocs) in 1 oven at 11am. Removed the quma that were in there and brought them back to the lab. Went back to totem, measured senescence. Moved the other half of prvi in ovens and B1 of quma out. Left for evo evo at 3pm.

\def\day{\textit{November 11th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Eco Evo

\def\day{\textit{November 12th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came back from eco evo. Worked on issues and model. Removed dirt B3 Left at 6pm. 

\def\day{\textit{November 13th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
Came in at 9. Removed half the prvi from the ovens and went to totem to finish measuring the pist. Also measured diameter for Bepa, except B3 because it was raining. Simulated data for a new wildchrokie model, and updated some issues. Worked fore 3 hours on proposal. Washed B3 for Pist. Left at 6

\def\day{\textit{November 14th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe, Tess and Nolan}
Came in at 9:30. Brought the xterra to totem with the shop vac. Nolan, Tess and I measured height for Bepa and the last bloc diameter for bepa. We brought back Pist B3 and placed them in 2 ovens because they are too big. We weighted all prvi and measured the red paint because the measurements from winter2025 were from the bottom of the mark, not the top, so I'll have to substract these measurements from those. Quma still need to be wheighted. Came back to the office, finished first proposal draft.

\def\day{\textit{November 17th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
TA work for quizz this morning. Came in at 10 and Tess and I weighted B1 and B2 for Quma. Then I met with Mao and Victor to discuss provenance pop up and decide on goals. Then I removed the pines from the ovens and realized that they were loosing a lot more needles than I would imagine... I updated the biomass issue to discuss this. Worked on crossdating for the rest of the day. At 5, I went to Totem and cleaned the very disgusting room that was filled with roden poop and pee. Left at 6pm.

\def\day{\textit{November 18th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Statistical rethinking. Worked on Wildchrokie model, egret pop up, ta quiz check, chl comparison issue and prior checks. Personal appointment at 3pm. Rand model during the night.

\def\day{\textit{November 19th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Statistical rethinking. Briefly chatted with Rob to discuss biomass of pines and we decided to be consistent that removing the needles from the pines weight would be ok. So I started removing needles from them which is extremelly time consuming. Updated crossdating issue and red a bunch of paper about it from Neil. Updated other issues and prepared my meeting with Victor in the evening. Went to Totem. Removed dirt from pist B1, washed the roots from B2 and started removing dirt from the birches. Left at 5:30

\def\day{\textit{November 20th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9am. Statistical rethinking. Brought back B2 pist and vaccum from Totem to forestry. Updated some issues. BUDR mingle. Worked on prior predictive checks and simulating data for fuelinex. Left at 6 and worked from home on chl comparison

\def\day{\textit{November 21st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Turned on the oven that has pist B2 in them. Statistical rethinking and worked on chl comparison all afternoon

\def\day{\textit{November 24th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe, Tess and Victor}
Came in at 9. Statistical rethinking, then went to Totem with Tess, monitored the last remaining trees for senescence and measured height for all segi, tried to measure diameter, but the caliper didn't work anymore. So measured height for poba 2 blocs, except B3 because it was raining too much. Came back to the office. Tried to fix my model for 4 hours, then went back to totem to remove dirt from Bepa. Victor came at 3:30 and helped me until 5:30pm. We got to remove all dirt for all bepas and B2 for Segi, which still need diameter measurement. 

\def\day{\textit{November 25th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Statistical rethinking. Then worked on trying to fix wildchrokie model that is still struggling with parameterization. Then went to totem, brought back B1 Pist, removed the B2 from the ovens (they were off since yesterday) and placed B1 in. TA meeting, then worked on Lizzie's comments on my thesis proposal. Worked on GDD model and on chlComparison.

\def\day{\textit{November 26th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Statistical rehinking. Weight Pist with Tess, brc seminar, worked on model, met with victor, attended Nick's defense practice and worked on model. Left at 6.

\def\day{\textit{November 27th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Worked on model all morning, then a little on my proposal. Met with Lizzie and worked a little on my model. Went to Totem to wash out the Bepa and Segi B2. Left at 6

\def\day{\textit{November 28th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe, Tess, Nolan and Mao}
Came in at 8:30. Grabbed the truck, met with Nolan and we packed the paper bags inside the truck and moved them to totem. Mao helped me a little. Tess came and we finished moving the birches inside the big ovens at totem. Came back to bring the segi upstairs and they were put in the ovens at 3pm. Worked on model all afternoon. I am not sure the ovens can reach 70 C at totem.
\def\day{\textit{November 29th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{November 30th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
