\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{September 1st 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked all day on model and preped for tomorrow's presentation. Looked at cores I set up during the weekend, about 50\% of them couldn't stitch

\def\day{\textit{September 2nd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Nolan}
Monitored senescence with Nolan. Took 3 hours. Set up up some cores.

\def\day{\textit{September 3rd 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking course. Worked on proposal. Sanded two bundles of cores. Set up for scan to batches of cores to scan. Attended first TA meeting. 

\def\day{\textit{September 4th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8. Met with Benjamin. Worked on model and finalized NSERC's application. Went to totem to weed bloc 1

\def\day{\textit{September 5th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8. Statistical rethinking, then submitted my NSERC's app and worked on model. Attended the TA workshop for a bit but left. 

\def\day{\textit{September 8th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. statistical rethinking course. Updated the chlorophyll issue, realized it's a non-linear relationship. Worked on model and met with Lizzie at 2 to talk about that. Left at 6 and went to weed bloc 2 at totem

\def\day{\textit{September 9th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked a bit on model from home, then came in the office at 10:30 and worked on my model for 1 hour. Worked on egret for 3 hours and updated my issues. Left at 5.

\def\day{\textit{September 10th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30, monitored budset at totem. At 10:15, went to egret check-in. 

\def\day{\textit{September 11th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on model pretty much all day, in the morning I worked from home. Sanded some cores and scanned some. 

\def\day{\textit{September 12th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Chatted with Lizzie, emails, et measured some cores in the afternoon (9 cores measured). Started a cleaning code too. Left at 6:30

\def\day{\textit{September 13th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked on cores and senescence photos. In 1 hour, I could measure 7 cores non-stop.

\def\day{\textit{September 15th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Statistical rethinking then worked on wildchrokie model, tried to get the priors into the stan code. Measured 3 cores and tried scanning 8 aefl (again) because tina failed over the weekend. Only 2 worked out of 8. Tried the chalk on two cores that couldn't get stitched and launched the scan. Left at 5. 

\def\day{\textit{September 16th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
Came in at 9:15. Recorded senescence by myself. Tess joined me at 10 and we finished at 12:30. Went back to the office and worked on measuring cores until the bayes working group. Left at 4:30\

\def\day{\textit{September 17th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 8:30. Nolan did budset monitoring. I worked on statistical rethinking and then updated all of my git issues and updated the stan code and wildchrokie model code. Went to the BRC symposium. Met briefly with Lizzie. I re-scanned twice the 2 cores I tried the previous day to scan and they didn't work. I set up 8 cores, tina failed. I re-set them up with some orange chalk, it didn't work again. I polished the sanding and re-set them for the night. Left at 6:30. 

\def\day{\textit{September 18th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Statistical rethinking. Left at 7.

\def\day{\textit{September 19th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9:30. Statistical rethinking, thesis proposal and worked on coringtreespotters cross-dating. Spent roughly an hour on non-centered parametization. Left at 6. 

\def\day{\textit{September 20th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{September 21st 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Finished measuring the last 4 cores

\def\day{\textit{September 22nd 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{September 23rd 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking and climate data

\def\day{\textit{September 24th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Egret in the morning. Spent all afternoon figuring out the cores that were tricky to measure. Left at 6:30

\def\day{\textit{September 25th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Came in at 9. Finished figuring out the tricky cores and fixed names and wrong tree rings measurements. Took most of the day. Started cross-dating. Went to tom booker's seminar. Weeded bloc 4 and replied to a bunch of issues. Left at 7.
\def\day{\textit{September 26th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{September 29th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe and Tess}
Senescence monitoring. Met with Lizzie. Worked on non-centered parameterization. left early because not feeling so well


\def\day{\textit{September 30th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
