\begin{center}
\section*{\month}
\end{center}

\def\day{\textit{August 1st 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Met with Devina in the morning to re-assess goals for shoot elongation and talk about tree core sanding. Worked on my model and met with Victor in the afternoon. Presentation on grad school and ice cream

\def\day{\textit{August 4th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Worked a bunch on my CGRS-D proposal and sent it to Lizzie

\def\day{\textit{August 5th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Met with Lizzie, bayes working group. Worked on model. Changed DPI resolution on Tina.

\def\day{\textit{August 6th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Took the day off

\def\day{\textit{August 7th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Started reading chapter 3 statistical rethinking. Started scanning some cores. Worked on proposal.

\def\day{\textit{August 8th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 11th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking in the morning. Worked on research proposal. Backed up photos greenhouse fisheye at totem.

\def\day{\textit{August 12th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Statistical rethinking in the morning. Worked on a research proposal. Worked on egret all afternoon. 

\def\day{\textit{August 13th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Monitored budset. Egret check in. Statistical rethinking and worked on proposal.

\def\day{\textit{August 14th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 15th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Devina and I did the last day of shoot elongation measurements! It was awful. Super rainy.

\def\day{\textit{August 18th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Met with Tim in the morning. Attended his talk. 

\def\day{\textit{August 19th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
First day of senesence monitoring! Only had time to monitor prvi and bepa. Monitored acne along by recording myself. Will finish tomorrow. 

\def\day{\textit{August 20th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Nolan monitored budset. I finished my first draft of my CGRS-D proposal. Finished monitoring senescence by voice recording since I ran out of time yesterday. 

\def\day{\textit{August 21st 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 22nd 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
Second round of chl measurements with Nolan. At 9:30 am. Started working on that model and worked on figures all afternoon. 

\def\day{\textit{August 23rd 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 24th 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 25th 2025}}
\def\weekday{\textit{Monday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 26th 2025}}
\def\weekday{\textit{Tuesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 27th 2025}}
\def\weekday{\textit{Wednesday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 28th 2025}}
\def\weekday{\textit{Thursday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 29th 2025}}
\def\weekday{\textit{Friday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 30th 2025}}
\def\weekday{\textit{Saturday}}
\subsection*{\weekday, \day}
\textbf {Christophe}

\def\day{\textit{August 31st 2025}}
\def\weekday{\textit{Sunday}}
\subsection*{\weekday, \day}
\textbf {Christophe}
